\documentclass[11pt]{article}
% Evidence claims: DD-C-0071 through DD-C-0088. Generated assets repeat the
% contributing claim IDs, immutable run IDs, and input checksum prefixes.
\usepackage[letterpaper,margin=0.92in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,booktabs,tabularx,array,enumitem,float,tikz,natbib,graphicx,xcolor}
\usepackage[hidelinks]{hyperref}
\definecolor{inktwo}{HTML}{25324A}
\definecolor{private}{HTML}{3C8D5A}
\definecolor{consensus}{HTML}{B75D7A}
\definecolor{planner}{HTML}{3977A8}
\definecolor{market}{HTML}{C98B32}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prb}{\mathbb{P}}
\newcommand{\ArtifactNote}[1]{\par\vspace{2pt}{\scriptsize\color{inktwo!72}#1}}
\newcommand{\Evidence}[1]{\par\noindent\textbf{Evidence status.} #1\par}
\newcommand{\Boundary}[1]{\par\noindent\textbf{Boundary.} #1\par}
\setlength{\parskip}{0.35em}
\sloppy
\title{\textbf{Threshold Discovery}\\[0.35em]\large Coordination, Crowding, and Minimum Viable Teams}
\author{Yohei Nakajima\\Untapped Capital}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Some discoveries require a team rather than a single successful action. This
changes the role of duplication. With a threshold of one, repeated actions are
pure crowding after the first attempt. With a threshold above one, overlap is
initially productive because an action does not count until a minimum viable
team forms. Too little coordination leaves stranded singletons; too much
coordination collapses the portfolio onto one candidate. This paper develops
that tension in a finite exact model and synthesizes six bounded components of
the Distributed Discovery program. A deterministic planner assigns minimum-size
teams to posterior-ranked candidates and obtains the sum of the largest
$\min\{\lfloor N/\tau\rfloor,M\}$ posterior masses. Strategic equal-split play
need not select that portfolio. Exact small-game enumeration contains weak pure
equilibria with zero discovery and distinguishes unilateral equilibrium from
pairwise and minimum-team stability. A dynamic extension shows that visible
actions can increase herding without increasing discovery in its registered
full-credit grid, while a separate threshold-two planner uses both team joining
and new-team formation. A mechanism census identifies authoritative,
eligibility, contribution, mediation, and matching rules that attain the
two-team planner recommendation in bounded common-posterior fixtures, while
also preserving equilibrium multiplicity and scope failures. DiscoveryBench v3
and a synthetic-only experiment package connect these results to auditable
evaluation and model-derived predictions. Every numerical statement is tied to
a checksum-validated immutable run and a claim record. No participants were
recruited, no human data were collected, and no experiment was conducted.
\end{abstract}

\noindent\textbf{Keywords:} threshold public goods; minimum viable teams;
coordination; crowding; collective search; distributed discovery.
\par\noindent\textbf{Publication status.} Working paper; not submitted, not
peer reviewed, and no DOI.

\Evidence{DD-C-0071, DD-C-0072, DD-C-0075, and DD-C-0076 are verified
theorem or identity claims. DD-C-0073, DD-C-0074, and DD-C-0077 through
DD-C-0087 are bounded exact results with the statuses stated in the claim
ledger. DD-C-0088 is a verified Monte Carlo estimate. Synthetic contrasts are
predictions, not observations.}

\input{generated/evidence-status.tex}

\section{Introduction}

Discovery is often modeled as if one correct attempt were enough. That is the
right abstraction for a single searcher opening a file, testing a molecule, or
checking a candidate answer. It is incomplete when action requires a team. A
field investigation may need two people for safety. An engineering experiment
may need several specialties before it can run. A multi-agent system may need a
minimum number of independent verifiers before a candidate is accepted. In
these settings, spreading every action across a different candidate produces
coverage but may produce no executable discovery at all.

The organizational problem becomes a portfolio problem with lumpy capacity.
Let $N$ agents choose among $M$ candidates, and let candidate $j$ count only if
at least $\tau$ agents choose it. A planner cannot simply maximize the number of
distinct actions. The planner must build viable teams. Yet forming teams does
not make concentration universally good. After the threshold is met, more
agents on the same candidate add no discovery value in the frozen model. The
right unit of diversification is therefore not the individual action but the
minimum viable team.

That observation creates three separate questions. First, what portfolio would
a planner choose when the posterior over candidates is known? Second, what
allocations can arise when agents choose strategically and share a discovery
prize? Third, which institutions can support a high-value team portfolio under
clearly stated information, authority, transfer, and deviation assumptions?
Treating those questions as one would conceal the difference between an
optimum, an equilibrium, and an implementation result.

The planner problem has a simple exact solution. No allocation can open more
than $\lfloor N/\tau\rfloor$ candidates, and no more than $M$ candidates exist.
Opening the posterior-ranked candidates is optimal. An attaining allocation
places exactly $\tau$ agents on each selected candidate before assigning any
leftovers. The value is
\begin{equation}
 V^{P}(\pi,N,\tau)=\sum_{j=1}^{\min\{\lfloor N/\tau\rfloor,M\}}\pi_{(j)},
 \label{eq:planner}
\end{equation}
where $\pi_{(1)}\geq\cdots\geq\pi_{(M)}$. This is an existence and value
theorem, not uniqueness: posterior ties and leftover agents may generate many
optimal assignments (DD-C-0071).

The strategic problem is less forgiving. When a target candidate opens, the
unit prize is split among agents on that candidate. An agent then compares its
share at the current occupancy with the share after a unilateral move. A pure
occupancy is a weak Nash equilibrium exactly when none of those finite moves
improves payoff (DD-C-0075). Weakness matters. If no candidate has reached the
threshold, one agent may be unable to create value alone. The resulting zero
payoff indifference can stabilize an allocation with zero discovery even while
the planner value is positive.

The paper also separates one symmetric mixed construction from the full
equilibrium correspondence. Uniform independent mixing over tied posterior
modes is always a symmetric mixed equilibrium for $\tau\geq2$ in the frozen
game, because a supported mode offers the same positive payoff and an
unsupported unilateral move cannot form a team. At $\tau=1$, an unsupported
candidate can instead pay its posterior mass immediately, so a precise outside
payoff condition is required (DD-C-0076). The selected mixture is useful for
comparison but is not a universal theory of equilibrium selection.

The synthesis adds time and institutions. In the dynamic model, agents observe
a shared clue, a private clue, and possibly earlier actions. Under full
duplicate credit, choosing a posterior mode at every reached information set is
a sequential Bayesian equilibrium (DD-C-0079). Exact bounded evaluation shows
that visible actions need not improve discovery and can increase herding
(DD-C-0081). Under a separately registered threshold-two planner, good policies
sometimes start a new singleton, sometimes join one, and sometimes reinforce
an already viable team (DD-C-0082). Timing does not erase the coordination-
crowding tradeoff; it makes the relevant action depend on the current portfolio.

Finally, institutions can change who is able or rewarded to form which team.
A ten-mechanism census distinguishes authority, recommendation, eligibility,
contribution rewards, and matching. Eight mechanisms attain the planner
portfolio in each of five common-posterior fixtures, while universal pooling
and sole-team rescue collapse to one candidate and do not (DD-C-0083). Some
strategic rules support the recommendation against unilateral and specified
two-person deviations, but retain many other pure equilibria (DD-C-0086).
Recommendation support is therefore not equilibrium selection.

The contribution is a disciplined map of the threshold-discovery problem. It
connects an exact planner theorem, bounded equilibrium and stability censuses,
dynamic attention, mechanism design, benchmark integration, and synthetic
predictions without upgrading any component beyond its evidence. The paper
makes no verified novelty claim. It is a working paper, not a DOI-bearing,
submitted, or peer-reviewed publication.

\section{Related literature}

Threshold discovery sits near several established literatures while using a
different objective. Threshold public-good and participation games study when
enough contributors coordinate to provide a good; early analyses emphasize
the sharp strategic effects of minimum participation requirements
\citep{PalfreyRosenthal1984,Diekmann1985}. Here the public outcome is not a
single project. Agents can form several candidate-specific teams, and the
planner values the posterior mass covered by the resulting portfolio.

Congestion and potential games study how payoffs change with resource occupancy
\citep{Rosenthal1973,MondererShapley1996}. Equal splitting in the present model creates a form of
crowding after a candidate is viable, but occupancy below the threshold is
complementary rather than congested. The same additional teammate can be
essential when occupancy rises from $\tau-1$ to $\tau$ and redundant when it
rises from $\tau$ to $\tau+1$. That sign change is the organizing feature of
the paper.

Coalition formation and hedonic grouping ask which collections of agents are
stable under different deviation concepts \citep{BogomolnaiaJackson2002}.
Cooperative-game concepts such as strong equilibrium and coalition-proofness
also distinguish individual from group deviations
\citep{Aumann1959,BernheimPelegWhinston1987}. The bounded census below uses
narrower registered objects: weak pure Nash, strict-member pair deviations,
and exact-size-$\tau$ strict-member deviations. It does not relabel those checks
as strong or coalition-proof equilibrium.

Information aggregation and organizational design study how shared evidence
changes action and coordination \citep{MarschakRadner1972,HellwigVeldkamp2009,
MyattWallace2012}. The Distributed Discovery framework emphasizes that better
group ranking can coexist with a worse portfolio of actions
\citep{Nakajima2026SharedDiscovery,WangEtAl2026DistributedDiscovery}. Thresholds
add a complementary constraint: maximal action diversity can also be useless
if no candidate receives enough effort to open.

Collective search and scientific division of labor ask how groups balance
exploitation and exploration \citep{March1991,Kitcher1990,Zollman2007}. The
finite model contributes a transparent capacity rule. When each discovery
requires $\tau$ agents, the planner has at most $\lfloor N/\tau\rfloor$ viable
search units. This supplies a compact benchmark for more elaborate dynamic,
heterogeneous, or costly-search models.

Mechanism design adds another distinction. A central assignment can implement
an allocation by authority. A mediator can recommend actions. A token or right
can condition prize eligibility. A contribution rule can reward membership in
an exactly minimal team. These are different institutional objects even when
their recommended allocations coincide. The paper therefore reports observed
information, action observability, commitment, transfers, subsidy, identity
selection, and deviation class rather than treating ``coordination'' as a
single intervention.

Coverage and welfare-sharing games ask how local utilities support or bound
system welfare \citep{Vetta2002,MardenWierman2013,PaccagnanChandanMarden2020}.
Those general utility-design results are essential collision checks for any
future implementation characterization. The current paper proves a planner
formula and audits specified bounded mechanisms; it does not establish general
marginal-contribution closure, price-of-anarchy optimality, or alignment of
every equilibrium.

\Boundary{The literature discussion locates the model; it does not certify
novelty. The formal and numerical claims of this paper are only those linked to
the repository claim ledger and immutable runs.}

\section{Threshold discovery model}

There is a finite candidate set $\mathcal M=\{1,\ldots,M\}$ and one hidden
target $\theta$. Conditional on the available evidence, the posterior is
$\pi=(\pi_1,\ldots,\pi_M)$ with positive entries summing to one. There are $N$
agents. Each agent chooses one candidate. Let $n_j$ be the occupancy of
candidate $j$, so $\sum_j n_j=N$.

A candidate is viable when $n_j\geq\tau$. Discovery is the event that the true
target is among the viable candidates. Conditional expected discovery is
therefore
\begin{equation}
 D(n;\pi,\tau)=\sum_{j=1}^{M}\pi_j\mathbf 1\{n_j\geq\tau\}.
 \label{eq:discovery}
\end{equation}
There is no additional value from occupancy above $\tau$, no execution failure
once the threshold is met, and no cost in the planner objective. Those
assumptions make the capacity logic exact. They also define the boundary of
the result.

For strategic analysis, the target candidate carries a unit prize divided
equally among agents who selected it, provided it is viable. An agent on
candidate $j$ obtains posterior expected payoff
\begin{equation}
 u_j(n)=
 \begin{cases}
   \pi_j/n_j,& n_j\geq\tau,\\
   0,& n_j<\tau.
 \end{cases}
 \label{eq:payoff}
\end{equation}
A unilateral move from $j$ to $k$ compares $u_j(n)$ with
$\pi_k/(n_k+1)$ if $n_k+1\geq\tau$ and with zero otherwise. This finite
comparison is the basis of DD-C-0075.

The mixed-action identity makes the same threshold visible probabilistically.
Suppose each of the other $N-1$ agents independently chooses $j$ with
probability $x_j$, and let $K_j\sim\mathrm{Binomial}(N-1,x_j)$. Choosing $j$
has expected payoff
\begin{equation}
 U_j(x)=V\pi_j\E\left[
 \frac{\mathbf 1\{K_j\geq\tau-1\}}{K_j+1}
 \right].
 \label{eq:mixed-payoff}
\end{equation}
At $\tau=1$, the share factor equals
$[1-(1-x_j)^N]/(Nx_j)$, with the exact zero limit equal to one. At $\tau=2$,
the $K_j=0$ term is removed and the zero limit is zero. These are verified
identities, not an equilibrium characterization (DD-C-0072).

Three benchmarks recur. Private clue-following sends each agent to the label
named by its clue. Common deterministic mode pools the clues and sends everyone
to a selected posterior mode. Registered tied-mode mixing makes independent
uniform draws over all posterior modes. The planner allocates minimum-size
teams to the highest posterior candidates. The first three rules turn evidence
into actions; the fourth is an allocation frontier. None should be called the
other.

\section{Minimum viable teams}

\subsection{The planner theorem}

Let $K=\min\{\lfloor N/\tau\rfloor,M\}$. Any allocation opening $q$ candidates
uses at least $q\tau$ agents, so $q\leq K$. Among all sets with at most $K$
candidates, the largest posterior mass is the sum of the $K$ largest entries.
Assigning $\tau$ agents to each of those candidates attains the bound, and any
leftover agents can be placed without closing an opened candidate. This proves
Equation~\ref{eq:planner} (DD-C-0071).

The proof yields an institutional rule of thumb: build the smallest teams that
can act, rank opportunities by posterior value, and diversify at the team
level. It does not say that every optimum has exactly the same occupancy.
Leftovers may move freely when they do not change viability. Posterior ties may
change which candidate labels are selected. If value continues to rise with
team size, execution can fail, or team members have heterogeneous skills, the
minimum-team construction need not remain optimal.

\subsection{The canonical phase diagram}

DD-016 freezes a canonical signal model with $M=16$, $N=8$, conditionally
independent clues, and clue accuracy $1/5$. Exact fraction arithmetic exhausts
490,314 labeled clue-count vectors. A materially different occupancy-orbit
enumeration reconstructs the same aggregates. Figure~\ref{fig:threshold-phase}
and Table~\ref{tab:threshold-phase} are generated directly from that immutable
output (DD-C-0073 and DD-C-0074).

\input{generated/threshold-phase.tex}

At $\tau=1$, individual diversity is useful because every distinct correct
action can discover. At $\tau=2$, many private or independently mixed actions
remain stranded as singletons. Common mode is still too concentrated, but the
gap between uncoordinated and coordinated portfolios changes. From $\tau=3$
through $8$, common mode and the registered tied-mode mixture exceed private
clue-following in the frozen fixture. Coordination becomes necessary to make
any candidate viable often enough.

The planner remains the appropriate frontier because it chooses whole teams.
For $\tau=1$ through $4$, it strictly diversifies beyond common mode and earns a
higher discovery value. For $\tau=5$ through $8$, only one viable coalition can
form with eight agents, so planner diversification cannot open a second
candidate and the planner ties common mode. The apparent convergence is a hard
capacity constraint, not evidence that universal concentration is generally
optimal.

\input{generated/threshold-table.tex}

The phase diagram also clarifies why ``crowding'' cannot be measured by raw
collisions alone. Some overlap is necessary: $\tau$ agents must coincide before
a candidate counts. Excess overlap is occupancy beyond what is needed to form
the viable teams in the selected portfolio. Failed subthreshold attempts and
excess members of already viable teams are different losses and demand
different interventions.

\subsection{Posterior ranking and action diversity}

Posterior ranking determines which teams the planner would form, not how
private agents come to share the same ranking. A common posterior can be an
input to an assignment problem. Dispersed private signals create an additional
information-design problem. The exact canonical census holds the signal
structure fixed and compares named action rules; it does not prove that pooling
information is always desirable or always harmful.

This separation matters operationally. An organization may have a high-quality
central ranking but lack assignment authority. It may have assignment authority
but unreliable execution. Or it may have decentralized signals that cannot be
truthfully aggregated. Equation~\ref{eq:planner} answers the allocation problem
conditional on the posterior. It does not solve the upstream acquisition and
reporting problems.

\section{Strategic equilibrium and selection}

\subsection{Pure occupancy equilibrium}

The pure equilibrium characterization is deliberately direct. An occupancy is
a weak Nash equilibrium if and only if every occupied agent weakly prefers the
current candidate payoff in Equation~\ref{eq:payoff} to every unilateral
destination payoff after adding one agent there. There are no other pure
unilateral deviations in the frozen action space, so the condition is necessary
and sufficient (DD-C-0075).

Weak equilibrium preserves economically meaningful coordination failures.
Suppose $\tau=2$ and every agent is a singleton. Each receives zero. A unilateral
move may create one viable pair, but whether it is profitable depends on the
destination posterior and resulting split. In other states, no single move can
create a team and all zero-payoff actions are tied. Removing such equilibria by
assuming strict tie-breaking would change the game rather than merely simplify
the analysis.

DD-017 registers eight positive rational posterior fixtures with $M$ between
two and four, $N$ between two and six, and every integer threshold from one to
$N$. It exhausts 3,728 occupancy states. An independent labeled-profile
enumerator visits 87,216 profiles, deduplicates their occupancies, and
reconstructs the same equilibrium correspondence.

\input{generated/equilibrium-census.tex}

In 52 of the 160 games, the worst weak pure equilibrium has zero discovery even
though the planner value is positive. Under the registered positive-over-zero
convention, the pure price of anarchy is infinite. This is a bounded exact
result, not a theorem that every threshold game has an inefficient equilibrium
(DD-C-0077).

\subsection{One symmetric mixture}

If $m$ candidates tie for the highest posterior and every agent independently
mixes uniformly over those modes, support payoffs are equal. For $\tau\geq2$,
an unsupported unilateral deviation cannot form a viable team and pays zero,
while a supported action has positive probability of joining enough other
agents. The mixture is therefore a symmetric mixed Nash equilibrium.

At $\tau=1$, an unsupported action immediately opens its candidate. The support
payoff must weakly exceed every unsupported posterior mass:
\begin{equation}
 \pi_{\max}\frac{1-(1-1/m)^N}{N/m}\geq \max_{k\notin S}\pi_k.
 \label{eq:mixed-boundary}
\end{equation}
The condition can fail. All 21 failures in the registered census occur at
$\tau=1$. This theorem verifies one symmetric construction but neither
characterizes all mixed equilibria nor supplies a learning or selection
process (DD-C-0076).

That qualification is essential when interpreting the canonical DD-016
tied-mode curve. The curve is a registered comparison rule. For thresholds two
and above it is also one equilibrium under the frozen equal-split game, but it
does not replace the full pure or mixed equilibrium correspondence. An
institutional recommendation must say which selection process, if any, makes
that curve behaviorally relevant.

\subsection{Coalitional stability}

Unilateral equilibrium does not settle whether a team can form by moving
together. DD-017 therefore asks two bounded questions. A pair blocks only if a
joint action change makes both named members strictly better. An exact-size-
$\tau$ coalition blocks only if a joint change makes every named member
strictly better. The two concepts coincide in coalition size when $\tau=2$ but
retain separate definitions.

Eight registered games have no pairwise-strict-stable weak pure equilibrium,
and 35 have no exact-size-$\tau$-strict-stable weak pure equilibrium
(DD-C-0078). These counts are not nested comparative statics. Exact-size
stability is not monotone in coalition size, and neither result tests arbitrary
coalitions, transfers, weak Pareto improvements, strong equilibrium, or
coalition-proofness.

The substantive lesson is methodological. A mechanism can pass unilateral
obedience while failing a team deviation. It can pass a minimum-team deviation
while retaining other bad equilibria. And it can be authoritative, making
deviation tests not applicable rather than passed. Those labels must remain
visible in any mechanism comparison.

\section{Dynamic attention}

Static occupancy hides the order in which agents observe and act. DD-015
freezes a three-target sequential model with two or three agents, one shared
clue, private clues, visible or hidden action history, and either fixed-budget
or stopping feedback. The reward in the autonomous game is full duplicate
credit: an agent receives one whenever its own action is correct, regardless of
what others do.

Under that reward, an agent's expected payoff from action $a$ is exactly its
posterior probability that $\theta=a$. Later actions do not change that payoff.
Choosing a posterior mode at every reached information set is therefore a pure
sequential Bayesian equilibrium, with the registered lowest-label tie-break
(DD-C-0079). This proposition does not extend to the equal-split threshold game
or to contribution and rescue rewards.

The exact grid contains 64 objective rows. The common-payoff planner strictly
exceeds autonomous full-credit play in 38. Autonomous agents follow a previous
action with positive probability in 32 rows and lean against a repeated prior
action with positive probability in 50. Stopping reduces expected actions
relative to fixed budget in every one of 32 parameter cells (DD-C-0080).

\input{generated/dynamic-summary.tex}

The visibility result is a preserved bounded null. Across 32 fixed-budget
cells, visible-action inference improves neither discovery nor expected action
dispersion relative to a history-hidden Bayesian baseline. It strictly lowers
both in 18 cells and ties in 14 (DD-C-0081). Earlier actions carry information,
but under full duplicate credit each agent optimizes individual correctness.
Informational value and portfolio value can therefore move in opposite
directions.

Stopping feedback is different because continuation reveals failure as well
as the earlier action. The fixed-budget visibility comparison excludes this
extra signal. Combining the two would make the negative result appear broader
than the registered design.

The threshold-two extension is separately registered and planner-only. With
three sequential agents and $\tau=2$, stopping preserves the fixed-budget
optimal discovery value while strictly reducing expected actions in all 16
parameter cells. Across its 32 objective rows, optimal policies use each of
five action categories with positive probability: start a singleton, join a
singleton, join a viable team, follow the shared clue, and oppose it
(DD-C-0082).

Joining a viable team after discovery is already secured can occur under fixed
budget because remaining actions must still be assigned. Its presence is not
evidence of decentralized over-crowding. Conversely, starting a singleton is
not automatically wasteful: it can preserve an option for a later agent. The
dynamic state determines whether another action completes a team, preserves a
portfolio, or becomes redundant.

\section{Mechanisms for team formation}

DD-018 fixes three candidates, four agents, threshold two, and five weakly
descending common posterior fixtures. The planner wants two teams of two on the
top candidates. Ten institutions are registered with explicit information,
observability, commitment, transfers, subsidy, anonymity, identity selection,
and deviation class.

Central assignment and random matching are authoritative after assignment.
Their planner performance comes from control, so post-assignment unilateral
obedience is not applicable. Team tokens and exclusive coalition rights make
prize eligibility depend on identity or charter. A correlated mediator sends
private recommendations without binding action. Universal pooling uses ordinary
threshold-adjusted equal splitting at a common lexicographic mode. Sole-team
rescue pays only when exactly one viable team exists. Marginal coalition
contribution pays an exactly minimal viable team. A threshold-adjusted
equal-split recommendation and a pairwise matching market complete the
registry.

\input{generated/mechanism-table.tex}

Across 50 mechanism-fixture rows, 40 recommendations attain the two-team
planner value. Central assignment, random matching, team tokens, exclusive
coalition rights, correlated mediation, marginal coalition contribution,
threshold-adjusted equal split, and the pairwise matching market attain it in
all five fixtures. Universal pooling and sole-team rescue attain it in none
(DD-C-0083).

Among 35 rows where unilateral action changes are meaningful, 31
recommendations are strictly obedient. Twenty-nine withstand every registered
strict-member pair deviation and every exact-size-two $\tau$-player deviation.
All 50 rows satisfy nonnegative participation, weak prize-budget balance, and
zero external subsidy (DD-C-0084). Report truthfulness is not applicable because
the common posterior is an input, not elicited from private reports.

The negative mechanism result is as informative as the successes. Universal
pooling and sole-team rescue place all four agents on the top candidate and
earn strictly less discovery than the two-team planner in every fixture.
Universal-pooling collapse is strictly unilaterally obedient in all five
fixtures but pairwise stable in only one. Sole-team-rescue collapse is strictly
unilaterally obedient and pairwise stable in all five (DD-C-0085). Even a
locally stable reward can preserve global concentration.

Team tokens, exclusive coalition rights, and marginal coalition contribution
support the two-team recommendation with strict unilateral obedience, no
registered strict-member pair or size-two block, weak budget balance, and no
subsidy in every fixture. Yet their labeled pure-Nash multiplicities are 25,
25, and 21 in every fixture (DD-C-0086). Supporting one good recommendation
does not imply uniqueness or a process that selects it.

The mechanism census suggests an architecture rather than a universal winner.
Where authority is legitimate, assignment can directly build minimum teams.
Where action remains voluntary, eligibility or marginal contribution can alter
the private payoff from joining the intended team. Where identities should be
anonymous ex ante, a mediator or random matching can distribute roles. Each
option trades autonomy, information requirements, and selection risk.

\Boundary{The mechanism evidence is a five-fixture exact common-posterior
census. It does not establish private report truthfulness, arbitrary coalition
stability, coalition-proofness, endogenous source acquisition, or a general
implementation theorem.}

\section{Benchmark and synthetic predictions}

Program V4 integrates the exact results into DiscoveryBench v3 and a versioned
synthetic experiment package. These artifacts serve different purposes. The
benchmark checks whether capability-declared protocols reproduce registered
exact task vectors. The experiment package maps model contrasts into treatments,
outcomes, hypotheses, and conditional power calculations. Neither is a field
evaluation.

DiscoveryBench v3 preserves every v1 and v2 exact vector while extending the
opt-in registry to 24 tasks, 29 protocols, and 39 metrics. Thirty-six compatible
pairs reproduce their exact registered values. The other 660 of 696 candidate
pairs remain explicit exclusions. Missing metrics are not imputed, hidden
target-state access is rejected, and no universal composite score is defined
(DD-C-0087).

Synthetic Experiment v3 preserves the earlier registries and shared-seed v2
power rows while extending the package to 37 treatment cells, 20 hypotheses,
23 outcomes, 14 response scenarios, 1,184 balanced synthetic assignments, and
1,680 power rows with 1,000 replications each. Among 840 registered rows at
sample sizes 640 or greater, 644 remain below the 0.80 calibration threshold.
Every failure is retained (DD-C-0088).

\input{generated/integration-table.tex}

The threshold and dynamic treatments are predictions about contrasts, not
claims about people. The favorable rational-response scenario at sample size
960 gives estimated powers 1.000, 0.999, 0.918, 0.948, 1.000, and 0.999 for
H15 through H20. Those values depend on the declared assumed effects, normal
sampling approximation, Bonferroni family alpha, response multiplier, and
fixed random streams. A different behavioral response model can produce much
lower power.

\input{generated/prediction-table.tex}

The experimental design is intentionally honest about failure. A power row
below 0.80 is not evidence that a treatment has no effect, just as a high
synthetic power estimate is not evidence that it does. The table is a planning
calculation conditional on synthetic assumptions. No participants were
recruited. No human data were collected. No experiment was conducted.

The benchmark likewise does not rank arbitrary agents. It evaluates only
compatible task-protocol-metric combinations. A protocol that lacks an input
capability is excluded rather than assigned a poor score; a protocol with
forbidden target-state access is excluded rather than rewarded. This keeps the
exact matrix interpretable and prevents a convenient aggregate from hiding
incommensurable tasks.

\section{Institutional implications}

\subsection{Form teams, then diversify teams}

The planner theorem provides the simplest design principle. When success needs
$\tau$ agents and additional members add no value, the scarce resource is the
number of viable teams, not the number of individuals. Organizations should
first make teams viable and then place successive teams on posterior-ranked
candidates. This is the threshold counterpart of action diversification.

The principle is conditional. It applies when the posterior is available, team
members are interchangeable, execution is deterministic at the threshold, and
there is no scale value beyond it. A surgical team, research group, or model
ensemble may violate all of those assumptions. In such cases, the minimum-team
portfolio remains a baseline against which the value of heterogeneity,
redundancy, and scale can be measured.

\subsection{Measure stranded effort and excess crowding separately}

An occupancy below $\tau$ is a stranded attempt in the frozen one-shot model.
Occupancy above $\tau$ is excess crowding if those agents could instead complete
another valuable team. Aggregate concentration measures can mix the two. A
system can have low concentration yet no viable team, or high concentration
with exactly the overlap needed for execution.

Useful operational metrics therefore include the number of viable candidates,
failed subthreshold attempts, excess members on viable candidates, expected
largest crowd, and posterior mass opened. DD-016 reports all of these as exact
objects. DiscoveryBench v3 keeps the capabilities and metric definitions
separate rather than compressing them into one score.

\subsection{Do not confuse support with selection}

A recommendation can be obedient and still coexist with many other
equilibria. The mechanism census makes multiplicity visible. A deployment
claim should name not only a supported profile but also the assumed selection
process: authority, defaults, repeated adjustment, mediation, matching, or
some other rule. Without that process, ``implements'' may mean only that one
good equilibrium exists.

The same warning applies to the registered tied-mode mixture. It is one
symmetric equilibrium for thresholds above one, but it is not the complete
equilibrium set. Comparing its discovery value with the planner is informative
about that selection rule and nothing broader.

\subsection{Use dynamic observability deliberately}

Visible actions can convey information and simultaneously induce correlated
behavior. The DD-015 null shows no discovery or dispersion gain from visibility
in the registered fixed-budget full-credit grid. This does not justify hiding
all actions. It just rejects the assumption that more observed history must
improve portfolio discovery.

Stopping rules add a different signal: continuing reveals that earlier actions
failed. In the exact dynamic studies, stopping reduces expected actions while
preserving the relevant planner value in the threshold-two extension. Systems
should distinguish action visibility, outcome visibility, and continuation
feedback rather than bundle them as ``transparency.''

\subsection{Match rewards to contribution and rights}

Equal splitting can reward joining an already popular candidate. Eligibility
rights and marginal contribution can instead attach reward to the intended
team structure. The bounded mechanism results show that these devices can
support the two-team planner profile without external subsidy in the registered
fixtures. They also introduce identity, observability, and enforcement demands.

No rule is free. Tokens require allocation and verification. Coalition rights
name privileged identities. Contribution rewards require occupancy
observability and a definition of the minimal team. Mediation requires trusted
recommendations. Assignment requires authority. The institutional choice
should report these inputs and not only the achieved discovery number.

\section{Limitations}

The model has one hidden atomic target and a normalized posterior. Actions name
candidates directly. Agents are homogeneous in capacity, each takes one action,
and a candidate opens deterministically at a common integer threshold. There is
no partial progress, execution failure, false positive cost, learning spillover,
or value from effort above the threshold. Equation~\ref{eq:planner} is exact
inside that model and should not be exported without restating it.

The strategic game uses a unit target prize split among agents at a viable true
candidate. Other reward rules produce other equilibria. The pure equilibrium
theorem covers unilateral deviations; the bounded stability census covers only
strict-member pairs and exact-size-$\tau$ coalitions. Neither is a strong-
equilibrium or coalition-proof analysis.

The canonical threshold census uses one $M=16$, $N=8$, $p=1/5$ signal fixture.
Its phase changes are exact for that fixture but not universal comparative
statics. The equilibrium census uses 160 small rational games. Counts such as
52, 8, and 35 are bounded observations, not asymptotic laws.

DD-015 uses three targets and two or three sequential agents. Its autonomous
equilibrium relies on full duplicate credit and reached information sets. Its
visibility null excludes stopping feedback from the comparison. Its threshold-
two extension is planner-only and must not be described as decentralized
equilibrium evidence.

DD-018 takes a common posterior as input, so it cannot test report truthfulness.
Its threshold is two and its coalitional checks are correspondingly small. The
mechanism names denote exact registered rules, not every institution that could
use the same ordinary-language label. The finding that sole-team rescue fails
in five fixtures is not a theorem that rescue payments generally fail.

DiscoveryBench v3 is an exact internal benchmark, not a hosted leaderboard or
universal measure of agent quality. Synthetic Experiment v3 uses declared
effects and response scenarios. Its Monte Carlo estimates are conditional
planning evidence only. The 644 retained failures are part of the design record,
not behavioral null results.

Most importantly, there is no empirical validation. No participant,
organization, laboratory, or deployed multi-agent system was observed. Human
deployment would require separate ethics, consent, privacy, retention,
identification, pilot, and governance review. The paper supplies hypotheses and
auditable finite benchmarks, not causal evidence.

\section{Conclusion}

Threshold discovery replaces a simple diversity maxim with a portfolio rule.
When a candidate requires a minimum viable team, some duplication is necessary.
The planner forms the smallest viable teams on posterior-ranked candidates.
Uncoordinated diversity can strand effort, while common-mode concentration can
waste team capacity. The relevant design objective is disciplined overlap.

Strategic behavior complicates that planner rule. Weak equilibria can have zero
discovery. One natural symmetric mixture is only one selection. Pair and
minimum-team stability answer different questions. Dynamic observability can
increase herding without increasing discovery. Mechanisms can support a good
portfolio while retaining many other equilibria.

The practical message is correspondingly precise: identify the minimum viable
team, measure both stranded attempts and excess crowding, diversify whole teams,
and state the authority and reward system that makes the portfolio credible.
Benchmark capability and calibration failures should remain visible. None of
these prescriptions is an empirical finding until tested under a separately
authorized design.

Threshold Discovery is therefore a bridge between information and institution.
Evidence ranks opportunities; team technology determines the granularity of
action; incentives and authority determine which portfolio is actually formed;
feedback changes what later agents know. A discovery architecture is complete
only when all four are specified.

\appendix

\section{Evidence and reproduction map}

The paper uses seven immutable run IDs. DD-016 supplies the planner proof audit,
payoff identities, canonical metrics, and eight-row phase diagram. DD-017
supplies the 160-game equilibrium and coalition census. DD-015 supplies one
baseline dynamic run and a separately labeled threshold-two extension. DD-018
supplies the ten-mechanism, five-fixture census. DD-010 and DD-011 supply the
versioned benchmark and synthetic experiment integration.

Each generated asset prints its contributing claim IDs, run IDs, generator,
and input checksum prefixes. Full checksums are stored in
`generated/provenance.json`. The builder first reads each immutable manifest,
requires passed validation and exit status zero, resolves the named output, and
compares its SHA-256 with the manifest. A missing or changed source stops the
build.

The claim audit extracts every token matching \texttt{DD-C-} followed by four digits
from the manuscript and generated assets, then resolves it against
\path{claims/claims.yml}. Citation keys are extracted from the manuscript and
resolved against the generated bibliography. Required sections and every
generated input are checked before compilation.

Tectonic compiles the manuscript twice with \path{SOURCE_DATE_EPOCH} fixed to the
DD-016 run start. The builder rejects nonzero exit status, undefined references,
undefined citations, and overfull boxes. The two PDF byte streams must have the
same SHA-256. Poppler supplies the page count and renders every page for visual
review. The committed validation record binds the source inputs, generated
assets, page count, and final PDF checksum.

\section{Exact claims by component}

DD-C-0071 is the general finite planner theorem. DD-C-0072 is the finite
binomial payoff identity. DD-C-0073 and DD-C-0074 are independently reproduced
canonical computational results. Their exact fractions, not displayed
decimals, determine all labels.

DD-C-0075 characterizes weak pure Nash occupancy in the frozen threshold game.
DD-C-0076 verifies one symmetric tied-mode mixture and its threshold-one
boundary. DD-C-0077 and DD-C-0078 report the bounded welfare and coalition
censuses. The latter do not imply strong or coalition-proof equilibrium.

DD-C-0079 proves the full-credit dynamic posterior-mode equilibrium. DD-C-0080
is the exact dynamic planner and response census. DD-C-0081 preserves the
visible-action herding null. DD-C-0082 is a separate planner-only threshold-two
extension.

DD-C-0083 through DD-C-0086 are exact bounded mechanism results. Their
verification uses all 81 labeled action profiles per fixture and an independent
4,050-entry action table. Applicability labels are part of the evidence: an
authoritative assignment does not ``pass'' a voluntary deviation test.

DD-C-0087 is the independently reproduced DiscoveryBench v3 exact matrix.
DD-C-0088 is a verified seeded Monte Carlo estimate. The latter has no
exactness basis and reports power and intervals to six decimals from rejection
counts. These categories are not interchangeable.

\section{Design checklist for applications}

An application should specify at least the following before using the model as
a benchmark:
\begin{enumerate}[leftmargin=2em]
\item the candidate set and posterior or signal channel;
\item the number, skills, and action capacity of agents;
\item the threshold and whether it varies by candidate;
\item execution probability and value above the threshold;
\item costs of stranded attempts, false positives, and redundant members;
\item what information each actor observes and when;
\item whether actions and outcomes are public, delayed, or private;
\item who has assignment authority and whether recommendations bind;
\item the reward, transfer, subsidy, and budget rules;
\item the relevant unilateral and coalitional deviation classes;
\item the equilibrium or learning selection process;
\item the metrics that remain incomparable and therefore unaggregated.
\end{enumerate}

Failing to specify these dimensions invites category errors. A planner value
may be reported as an equilibrium. An authoritative assignment may be reported
as voluntary obedience. Pair stability may be reported as coalition-proofness.
A synthetic power estimate may be reported as a behavioral effect. The
repository's evidence policy treats each of those upgrades as invalid.

\section{Interpretive cases}

Consider first a team with $N=8$ and threshold $\tau=2$. Capacity permits four
viable teams. If the posterior has four clearly dominant candidates, the
planner places a pair on each. A policy that places eight agents on the top
candidate spends three team-equivalents without opening any additional target.
A policy that sends every agent to a different candidate opens none. Both can
be described as coordinated in ordinary language, but only the four-pair
portfolio uses capacity efficiently under the frozen objective.

Now consider $N=8$ and $\tau=5$. Only one viable team can form. The planner
opens the top posterior candidate, and the remaining three agents cannot form a
second team. Here common-mode concentration and the planner discovery value
coincide. The tie follows from capacity. It does not imply that extra members
add value, nor does it generalize to a larger team or smaller threshold.

In a decentralized threshold-two game, two agents may have to move together to
create a profitable alternative. Unilateral obedience therefore cannot certify
resistance to pair deviations. Conversely, passing every named pair deviation
does not test three-person changes or deviations with transfers. The deviation
class is part of the result, not a footnote.

In a dynamic setting, an earlier action changes both the posterior and the
portfolio state. Following may exploit information but increase crowding.
Opposing may diversify action but ignore a strong signal. Joining a singleton
can complete a team; starting a singleton can create an option; joining a
viable team can be redundant. A sensible policy must condition on all three
objects: belief, occupancy, and remaining action capacity.

Finally, compare a central assignment with a token mechanism. Both may support
the same two-pair portfolio. The assignment uses authority, so voluntary
obedience after commitment is not the relevant test. Tokens preserve action
choice but restrict prize eligibility, so obedience and equilibrium
multiplicity matter. Reporting only expected discovery would erase the central
institutional difference.

\section{Prediction and measurement boundaries}

The synthetic experiment extension maps the theory to registered contrasts.
It can ask whether team tokens change viable-team formation, whether visible
history changes herding, or whether stopping feedback reduces expected actions.
The power calculation requires an assumed effect and response model. It cannot
tell whether participants understand the institution, whether identities
create fairness concerns, or whether the experimental task represents a real
organization.

Outcome measurement should preserve the portfolio decomposition. Discovery
alone cannot distinguish a lucky concentrated policy from systematic team
formation. Expected distinct actions alone rewards stranded singletons. Useful
outcomes include viable-candidate count, posterior mass opened, failed
subthreshold attempts, excess overlap, largest crowd, action count, and the
distribution of rewards. No one of these is a universal composite score.

The benchmark and experiment package also preserve version boundaries.
DiscoveryBench v1 and v2 remain unchanged prefixes of v3. Synthetic Experiment
v1 and v2 remain public alongside v3, and shared-seed v2 power rows are exactly
preserved. Versioning makes changes auditable without rewriting earlier
evidence.

Human deployment remains outside the current program. A future study would
need a new issue and registration specifying ethics, consent, privacy,
retention, recruitment, exclusion, stopping, identification, and governance.
Nothing in the present PDF authorizes that work.

\section{Planner proof and equilibrium audit detail}

The planner proof can be read as an upper bound followed by a construction.
For any occupancy $n$, let $O(n)=\{j:n_j\geq\tau\}$ be the opened set. Since
each opened candidate consumes at least $\tau$ agents,
$|O(n)|\tau\leq N$. Thus $|O(n)|\leq\lfloor N/\tau\rfloor$. The opened set is
also a subset of $M$ candidates, so its cardinality is at most $K$. Posterior
ranking then gives
\begin{equation}
 D(n;\pi,\tau)=\sum_{j\in O(n)}\pi_j
 \leq \sum_{j=1}^{K}\pi_{(j)}.
\end{equation}
Assigning exactly $\tau$ agents to each ranked candidate $1$ through $K$ opens
that set. The number used is $K\tau\leq N$. Placing the remaining
$N-K\tau$ agents anywhere cannot close an opened candidate, so the bound is
attained. The argument uses no continuous relaxation and no limiting step.

The DD-016 hand audit tests this theorem on 63 small allocation problems. Three
posterior fixtures are crossed with $N=1$ through $6$ and every admissible
threshold. Exhaustive enumeration computes the best value independently of the
closed form. It also checks normalization and upper and lower bounds. These
finite tests do not prove the theorem, but they make common implementation
errors hand-detectable: forgetting the minimum with $M$, assigning a partial
team, or treating leftover occupancy as an additional opened candidate.

The payoff identity has a similarly direct finite derivation. For $x_j>0$,
the binomial coefficient relation
\begin{equation}
 \frac{1}{k+1}{N-1\choose k}=\frac{1}{Nx_j}{N\choose k+1}x_j
\end{equation}
turns the expected equal share at threshold one into
$[1-(1-x_j)^N]/(Nx_j)$. At threshold two, the $k=0$ term is excluded, producing
the registered subtraction of $(1-x_j)^{N-1}$. Exact endpoint handling matters:
the threshold-one zero limit is one, while the threshold-two zero limit is zero.

The pure-equilibrium verifier does not rely on occupancies alone. The primary
method enumerates aggregate states and applies every candidate-to-candidate
unilateral comparison. The independent method enumerates labeled action
profiles, evaluates every named agent's deviation, and deduplicates the
surviving occupancies. Agreement between 3,728 aggregate states and 87,216
labeled profiles protects against multiplicity errors that could be hidden by a
single representation.

Coalitional verification changes representation again. The primary evaluator
names each coalition and enumerates joint destination actions. The independent
method removes a coalition from an occupancy, enumerates possible additions,
and solves the exact payoff-compatible matching problem between named members
and destination slots. A removed equilibrium, altered best value, and changed
pair-stability label are targeted corruption tests. Passing them supports the
bounded census, not a claim beyond its registry.

\section{Institutional audit matrix}

The mechanism comparison is easiest to interpret as a matrix of questions.
First ask whether the institution controls action. Central assignment and
authoritative matching do. Their planner values are allocation results, and a
post-commitment deviation test would be a category error. The pairwise matching
market binds action within a selected pair but leaves pairs to choose among
candidates, so pair-level equilibrium remains relevant.

Second ask whether eligibility changes with identity. Team tokens condition
the prize on a fixed balanced token endowment. Exclusive coalition rights name
the coalition entitled to the candidate prize. Both can make a deviation
unattractive even when the physical action is available. This can support the
intended portfolio, but it requires verifiable identity and a legitimate rule
for allocating the scarce rights.

Third ask whether recommendations are private and correlated. The correlated
mediator randomizes over balanced teams and sends individual recommendations.
Its ex ante anonymity differs from a fixed named assignment. Obedience is a
posterior comparison conditional on the recommendation. The bounded result does
not show that agents truthfully report private signals to the mediator because
the registry starts from a common posterior.

Fourth ask what contribution earns the prize. Universal pooling splits among
all agents at the successful viable target. Sole-team rescue conditions payment
on having exactly one viable team. Marginal coalition contribution restricts
payment to an exactly minimal viable team. Threshold-adjusted equal split uses
the ordinary team share at the recommended two-pair portfolio. Similar
recommendations can therefore rest on different counterfactual rewards.

Fifth ask which deviations were actually evaluated. The census records
unilateral changes, named pair changes, and exact-size-two threshold-team
changes where they apply. A block requires strict improvement for every member.
It does not allow side payments or count a weak improvement for one member.
Those choices preserve a finite exact audit but leave larger coalitions and
other stability concepts open.

Finally ask what happens away from the recommendation. The complete 81-profile
table for each fixture and mechanism counts all labeled pure equilibria under
the registered rule. High multiplicity is not a verification failure. It is an
institutional risk that would be lost if the audit reported only whether the
planner profile is supported. The correct conclusion is conditional: several
rules support a high-discovery team portfolio in the frozen fixtures, while no
selection theorem identifies that portfolio as the unique realized outcome.

\section{Preserved failures and open questions}

The evidence program retains failures because they determine what the paper
cannot claim. The canonical threshold result includes regimes where common
mode raises discovery relative to private clue-following and regimes where it
lowers it. Reporting only one side would turn a phase diagram into a slogan.
The capacity transition at threshold five is equally important: once only one
team can form, the diversified planner cannot improve on a correctly selected
common mode in the frozen model.

The equilibrium census retains weak zero-discovery equilibria. They are not
removed because they produce an inconvenient infinite price-of-anarchy label.
It also retains 21 failures of the tied-mode mixed rule, all at threshold one.
Those failures identify exactly why the unsupported-action condition in
Equation~\ref{eq:mixed-boundary} is necessary.

The dynamic program retains the visibility-herding null. Visible histories
strictly lower discovery and dispersion in 18 fixed-budget cells and tie in the
other 14; there is no registered cell where they improve either outcome. That
result is bounded, but it rules out presenting action visibility as uniformly
helpful within the declared grid. The threshold-two extension remains labeled
planner-only because no decentralized threshold equilibrium was solved there.

The mechanism program retains the two concentrated failures. Universal pooling
and sole-team rescue do not attain the two-team planner value in any of the five
fixtures. It also retains multiplicity for mechanisms that support the planner
recommendation. A passing obedience check is not converted into uniqueness.
Not-applicable truthfulness and authority fields remain not applicable rather
than being counted as favorable results.

The benchmark retains 660 capability exclusions. The experiment package
retains 644 large-sample calibration failures. Neither artifact fills missing
values with convenient defaults. This makes the public surface less compact but
keeps the inference boundary reviewable.

Several questions remain open. Heterogeneous team skills may make a team worth
more than the sum of interchangeable members. Candidate-specific thresholds
may change posterior ranking into a knapsack problem. Stochastic execution may
create value above the minimum team size. Endogenous source acquisition may
couple who learns with who acts. Private posteriors require an elicitation and
truthfulness layer absent from DD-018. Larger coalitions and transfers may
overturn pairwise stability. Learning dynamics may select equilibria that the
static census merely lists.

These extensions should not be answered by stretching the present labels. Each
requires a new registered model, resource estimate, verifier, and evidence
category. A new numerical claim would require a new immutable run; a new
theorem would require a proof and proportional tests. Until then, they remain
questions rather than implied conclusions.

\bibliographystyle{plainnat}
\bibliography{generated/references}

\section*{Artifact declaration}

This document is a project-authored working paper distributed under the
repository's MIT license. It has no DOI, has not been submitted, and has not
been peer reviewed. It makes no verified novelty claim. The bibliography
positions the model against established literatures; it is not a novelty
certificate.

The authoritative numerical sources are these immutable runs:
\begin{itemize}[leftmargin=2em,itemsep=0pt,topsep=2pt]
\item \path{20260722T021526Z_DD-016_00271ff8_123b2809e3};
\item \path{20260722T024032Z_DD-017_033452f6_3d2c74fdfb};
\item \path{20260722T043713Z_DD-015_92d53ac1_0e7cf1ec0a};
\item \path{20260722T044453Z_DD-015_34bc4379_33e1da478b};
\item \path{20260722T051847Z_DD-018_a193f602_3b3ddac173};
\item \path{20260722T054447Z_DD-010_d265e480_6930915b02}; and
\item \path{20260722T061958Z_DD-011_5743ccba_19b6517655}.
\end{itemize}
They must not be rerun for freshness.

Reproduction requires the pinned repository dependencies, Tectonic, and
Poppler. \path{make threshold-discovery} validates input checksums, regenerates eight
assets, resolves claim and citation keys, compiles twice under a fixed source
epoch, rejects unresolved references and overfull boxes, and requires byte-
identical PDFs. Any source or PDF checksum change invalidates the visual review
and requires a complete rebuild and all-page inspection.

No participants were recruited. No human data were collected. No experiment
was conducted.

\end{document}
