\documentclass[12pt]{article}
% Evidence claims: DD-C-0089 through DD-C-0110. Generated assets repeat the
% contributing claim IDs, immutable run IDs, and input checksum prefixes.
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,booktabs,tabularx,array,enumitem,float,tikz,natbib,graphicx,xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\usetikzlibrary{positioning,arrows.meta}
\definecolor{inktwo}{HTML}{25324A}
\definecolor{private}{HTML}{3C8D5A}
\definecolor{shared}{HTML}{B75D7A}
\definecolor{planner}{HTML}{3977A8}
\definecolor{accent}{HTML}{C98B32}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prb}{\mathbb{P}}
\renewcommand{\path}[1]{\texttt{\detokenize{#1}}}
\newcommand{\ArtifactNote}[1]{\par\vspace{2pt}{\scriptsize\color{inktwo!72}#1}}
\newcommand{\Evidence}[1]{\par\noindent\textbf{Evidence status.} #1\par}
\newcommand{\Boundary}[1]{\par\noindent\textbf{Boundary.} #1\par}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\setlength{\parskip}{0.35em}
\setlength{\parindent}{1.2em}
\linespread{1.06}
\sloppy
\title{\textbf{When Does Information Sharing Improve Decentralized Discovery?}\\[0.35em]\large Aggregation, Independent Rescue, and Equilibrium Selection}
\author{Yohei Nakajima\\Untapped Capital}
\date{July 2026}

\begin{document}
\maketitle
\input{abstract.tex}

\noindent\textbf{Keywords:} information sharing; decentralized discovery;
portfolio search; information aggregation; equilibrium selection; organizational design.

\Evidence{The manuscript synthesizes DD-C-0089 through DD-C-0110 without
creating a new scientific claim. Analytic identities and theorems, independently
reproduced bounded computations, a verified bounded negative result, and a
verified equilibrium-selection failure retain their ledger statuses. The source
data are synthetic and model-generated.}

\section{Introduction}

Should searchers share what they know before acting? The familiar answer is that
sharing improves a group's estimate of which action is best. That answer is
incomplete when the outcome of interest is discovery by a portfolio of actions.
Sharing can make one common action more accurate while removing independent
attempts that could rescue a mistaken common choice. The organizational question
is therefore not whether the pooled posterior is better. It is whether its gain
is large enough to compensate for the search capacity absorbed by pooling.

This paper develops that comparison in four layers. First, an action-budget
profile records the best centralized discovery probability obtainable from a
pooled signal when the planner may take one, two, or more posterior-ranked
actions. Second, an incremental-sharing identity decomposes a move from $s$ to
$s+1$ pooled agents into the improvement of the pooled block and the loss of one
private rescue action. Third, a residual-error theorem gives the exact frontier:
sharing helps precisely when the pooled error contracts faster than the rescue
technology can repair it. Fourth, a binary Bayesian game shows why a positive
selected-equilibrium result does not settle the decentralized implementation
question.

The central nonstrategic identity is especially transparent. Let $C_s$ be the
probability that the correct candidate is covered by the action budget assigned
to a pooled block of $s$ agents. If each of the remaining $N-s$ independent
searchers succeeds with probability $q$, the registered protocol yields
\begin{equation}
  G_s=1-(1-C_s)(1-q)^{N-s}.
  \label{eq:incremental-value}
\end{equation}
Writing $e_s=1-C_s$, an additional sharing step satisfies
\begin{equation}
 G_{s+1}-G_s=(1-q)^{N-s-1}\big[(1-q)e_s-e_{s+1}\big].
 \label{eq:frontier-intro}
\end{equation}
Thus the step helps if and only if $e_{s+1}/e_s<1-q$, is neutral at equality,
and hurts above the threshold. The statement is exact under the stated rescue
protocol (DD-C-0092 and DD-C-0097). It is not a theorem that more accurate
signals always help, nor is it a comparison of arbitrary information structures.

The binary strategic result supplies a genuine positive sharing interval. Two
agents receive individually accurate clues with $p=3/5$ from a hidden mixture of
a common-source branch and an independent-source branch. The realized branch is
not revealed. Under the registered anonymous, label-equivariant private
equilibrium and the posterior-only identical-mixing shared equilibrium, sharing
strictly improves selected discovery exactly when
\begin{equation}
 \rho\in\left(\frac{5\sqrt{73}-17}{48},1\right).
 \label{eq:positive-interval}
\end{equation}
The same interval improves selected per-agent payoff (DD-C-0106 and
DD-C-0107). This is a coordination-free positive result: no planner assigns
targets and no binding recommendation is added when signals are shared.

The qualification is equally central. The positive interval is
selection-dependent and is not an every-equilibrium result. For every dependence
level, private play also has opposite constant-target pure equilibria that attain
discovery one. After sharing, ownership-aware disagreement strategies can split
targets without being functions only of the common posterior. Those alternatives
show that posterior-only identical mixing is a selection, not the whole strategy
space (DD-C-0109). A centralized top-two planner also obtains discovery one and
strictly dominates the selected shared outcome (DD-C-0110). The positive theorem
and the selection failure are presented together because separating them would
overstate what information sharing implements.

\input{figures/architecture.tex}

Three further exact findings organize the analysis. One-person accuracy is not a
sufficient statistic for portfolio value: two half-accurate channels can have the
same direct private discovery yet opposite sharing directions and different
centralized recovery budgets (DD-C-0089--DD-C-0091). Full action capacity always
recovers at least the direct private baseline, but the minimum recovery budget
depends on the entire signal geometry (DD-C-0098 and DD-C-0101). Finally, a
complete 177-scenario registry contains compression, aggregation, and all-neutral
curves but no mixed curve. The zero is preserved as a bounded negative result,
not promoted to a general monotonicity theorem (DD-C-0099--DD-C-0103).

The paper contributes a theorem-family synthesis rather than a novelty claim.
Decision theory studies comparisons of experiments \citep{Blackwell1953}; team
theory studies decentralized use of information \citep{Radner1962}; social
learning studies herding and cascades \citep{Banerjee1992,BikhchandaniEtAl1992,
AcemogluEtAl2011}; and information design studies the consequences of signal
structures and recommendations \citep{KamenicaGentzkow2011,BergemannMorris2016}.
Our narrower object is the composition of pooled posterior coverage, remaining
rescue actions, and equilibrium selection in finite discovery portfolios. The
literature search and evidence map distributed with the paper explain why broad
priority language would be unsafe.

The rest of the paper proceeds from definitions to geometry, the sharing
frontier, recovery, and strategic implementation. Every displayed numerical
asset is generated from checksum-validated immutable run outputs. Exact numbers
are labeled as fractions; decimals are displays. Centralized benchmarks,
decentralized protocols, selected equilibria, and alternative equilibria are not
interchanged.

\section{Discovery architectures and comparison baselines}

Let $\Theta=\{1,\ldots,M\}$ contain exactly one correct candidate. Discovery
occurs when at least one realized action equals the state. The objective is the
ex ante probability of discovery. A channel maps the state to a signal. Agents
may use signals privately, pool some signals, or submit them to a planner. The
same evidence can therefore enter architectures with different action authority.

\begin{definition}[Direct private baseline]
With $N$ private agents, each agent maps its own signal to one action under the
registered direct rule. The resulting discovery probability is $P_N$.
\end{definition}

\begin{definition}[Centralized action-budget profile]
Given all signals in a pooled block, let
\[
 V_L=\E\left[\sum_{j=1}^{L}\pi_{(j)}\right],
\]
where $\pi_{(1)}\geq\cdots\geq\pi_{(M)}$ are the ordered posterior masses and
$L\leq M$. The recovery budget is
\[
 L^*=\min\{L:V_L\geq P_N\}.
\]
\end{definition}

The definition separates information from capacity. $V_1$ measures the best
single common action after pooling. $V_L$ measures what a planner can cover with
$L$ distinct posterior-ranked actions. Neither number is the discovery of a
decentralized equilibrium unless an institution implements those actions.

\input{tables/channel-definitions.tex}

Four comparisons recur. The \emph{private baseline} allows autonomous direct
actions from private signals. The \emph{pooled centralized profile} gives a
planner the pooled posterior and an explicit action budget. The
\emph{incremental-sharing protocol} pools $s$ agents into a common block while
the others retain independent rescue actions. The \emph{strategic protocol}
lets agents maximize a shared discovery prize and requires an equilibrium rule.
These are different counterfactuals, not alternative estimators of one quantity.

The authority distinction matters for interpretation. A planner that chooses
the posterior top two can enforce diversification. Two autonomous agents who
see the same posterior still face a coordination problem: absent roles,
identifiers, or ownership-conditioned strategies, their symmetric response may
duplicate. Conversely, two private agents can coordinate on opposite constant
targets even without using their signals. That behavior is an equilibrium in
the registered binary payoff game but is not direct clue-following. Comparing
the wrong rows can reverse the verbal conclusion without changing any number.

The information structures themselves also differ. A point channel names one
candidate; a shortlist identifies a set; an exclusion signal rules out a
candidate; and a confidence point reports a candidate with a confidence class.
Set-valued prediction is studied as a controlled ambiguity problem
\citep{MortierEtAl2021,SadinleEtAl2019}. Here those geometries are useful because
they can hold one-person accuracy fixed while changing posterior rank mass and
therefore multi-action coverage.

\Boundary{The finite channels are registered synthetic objects. They are not
estimated representations of laboratories, firms, committees, or human teams.
The analysis compares discovery architectures within those objects.}

\section{Signal geometry is not one-person accuracy}

The first result is a sufficiency failure. One-person accuracy $q$ records the
probability that a direct action is correct. It discards how posterior error is
distributed across the remaining candidates. Yet a second or third action is
valuable precisely because of that distribution.

\begin{proposition}[Action-budget profiles; DD-C-0089]
In the frozen $M=4,N=3$ registry, the five channel families have the exact
profiles reported in \cref{tab:profiles}. In particular, the half-accurate noisy
point and guaranteed-shortlist channels both have $q=1/2$ and direct private
discovery $P_3=7/8$, but their centralized profiles are respectively
\[
 (V_1,V_2,V_3)=\left(\frac{7}{12},\frac{43}{54},\frac{25}{27}\right)
 \quad\text{and}\quad
 \left(\frac{17}{18},1,1\right).
\]
\end{proposition}

The computations are finite exact enumerations independently reproduced from
the registered model and fixtures. The proposition does not rank all point and
shortlist channels. It exhibits two channels for which equal accuracy and equal
direct private discovery fail to determine pooled portfolio value.

\input{figures/same-accuracy-profile.tex}
\input{tables/action-budget-profiles.tex}

\begin{corollary}[Accuracy is insufficient; DD-C-0090]
Neither one-person accuracy nor the pair $(q,P_3)$ determines the centralized
action-budget profile or the minimum recovery budget.
\end{corollary}

For the noisy point, one pooled action covers only $7/12$ and two cover $43/54$;
three are required to recover $7/8$. For the guaranteed shortlist, one pooled
action already covers $17/18$, so $L^*=1$. The exclusion and confidence-point
channels provide further distinct shapes: the former reaches certainty at three
actions, while the latter has high direct private discovery $485/512$ but needs
three pooled actions to recover it.

\begin{proposition}[Registered recovery budgets; DD-C-0091]
For noisy point, noisy shortlist, guaranteed shortlist, exclusion, and confidence
point, the recovery budgets are respectively $3,2,1,2,3$.
\end{proposition}

The result suggests a practical diagnostic. An organization considering pooled
evaluation should estimate or stress-test a coverage curve, not report only the
top-choice accuracy. If pooled evidence concentrates almost all posterior mass
on a small set, a modest common action budget can be enough. If its errors remain
diffuse or systematically compress plausible alternatives behind one label,
pooling may require many actions to restore the private portfolio baseline.

This diagnostic is related to, but not supplied by, Blackwell's comparison of
experiments. Blackwell dominance ranks experiments for every decision problem
with a single decision maker \citep{Blackwell1953}. The present comparisons hold
the discovery problem fixed while changing how many actions remain and who
controls them. A scalar accuracy ordering is weaker still. We therefore do not
describe the bounded registry as a universal information order.

\section{Aggregation gain and independent rescue}

Consider $N$ searchers. A pooled block of size $s$ produces coverage $C_s$ from
its assigned action budget. Each of the $N-s$ remaining private searchers has an
independent probability $q$ of rescuing a miss. Conditional on a pooled miss,
all private rescue actions fail with probability $(1-q)^{N-s}$. This yields
\cref{eq:incremental-value}.

\begin{theorem}[Incremental-sharing identity; DD-C-0092]
For $1\leq s<N$,
\[
 G_{s+1}-G_s=(1-q)^{N-s-1}\{(1-q)(1-C_s)-(1-C_{s+1})\}.
\]
Consequently the sign of an additional sharing step is the sign of the pooled
coverage gain net of the private rescue action it replaces.
\end{theorem}

\begin{proof}
Subtract $1-(1-C_s)(1-q)^{N-s}$ from
$1-(1-C_{s+1})(1-q)^{N-s-1}$ and factor the positive term
$(1-q)^{N-s-1}$. No distributional approximation is used.
\end{proof}

\begin{corollary}[Noisy point monotonicity; DD-C-0093]
For the registered noisy point family, the coverage improvement from adding a
signal does not overcome the lost rescue action; the incremental-sharing curve
is weakly decreasing on the proved parameter domain.
\end{corollary}

The corollary is channel-specific. It does not follow from $q=1/2$. The
registered guaranteed-shortlist channel has the same accuracy and moves in the
opposite direction.

\input{figures/incremental-curves.tex}
\input{tables/sharing-paths.tex}

\begin{proposition}[Opposite registered paths; DD-C-0094]
At $M=4,N=3,q=1/2$, the noisy-point path is
$7/8,3/4,7/12$, with changes $-1/8,-1/6$, whereas the
guaranteed-shortlist path is $7/8,11/12,17/18$, with changes
$1/24,1/36$.
\end{proposition}

Across 2,555 frozen rows, 1,848 adjacent moves are negative, 196 are neutral,
and none is positive for the noisy-point monotonicity census (DD-C-0095). Those
counts reproduce the theorem's sign on a bounded grid; they are not the proof.
The guaranteed-shortlist row is a verified counterchannel to any claim that
sharing must decrease simply because the private portfolio loses independent
actions (DD-C-0096).

The decomposition clarifies several verbal confusions. Sharing does not merely
``add information.'' It expands the pooled information set while changing the
portfolio's action structure. Nor does diversification merely ``waste'' the
pooled posterior: a low-ranked private action can be valuable precisely on the
event that the pooled block is wrong. The sign is controlled by the product of
these two margins.

\section{The General Sharing Frontier}

The identity becomes a general criterion after expressing coverage in residual
errors. Let $e_s=1-C_s$. When $e_s>0$, define the contraction ratio
$\rho_s=e_{s+1}/e_s$. The private rescue threshold is $1-q$.

\begin{theorem}[General Sharing Frontier; DD-C-0097]
Under the registered independent-rescue protocol,
\[
 \operatorname{sign}(G_{s+1}-G_s)
 =\operatorname{sign}\big((1-q)e_s-e_{s+1}\big).
\]
If $e_s>0$, the step strictly improves discovery exactly when
$\rho_s<1-q$, is neutral exactly when $\rho_s=1-q$, and strictly reduces
discovery exactly when $\rho_s>1-q$.
\end{theorem}

\begin{proof}
The first statement is \cref{eq:frontier-intro}; its prefactor is positive for
$q<1$. Dividing the bracket by $e_s>0$ gives the ratio criterion. If $e_s=0$,
pooled coverage is already one and the undivided expression governs the boundary.
\end{proof}

The theorem is a break-even rule. The new pooled signal must shrink residual
error by more than an independent private attempt would. A larger $q$ makes
rescue more powerful and lowers $1-q$, so pooling faces a stricter contraction
test. A weaker rescue technology raises the threshold and makes pooling easier
to justify. The result is deliberately architectural: changing dependence among
rescue actions or allowing the pooled block to control a different number of
actions changes the formula.

\input{figures/residual-frontier.tex}

The frontier reconciles apparently contradictory examples. The noisy point
compresses error too slowly relative to a half-accurate rescue action. The
guaranteed shortlist eliminates enough residual mass to compensate for losing
that action. Equal $q$ therefore places both examples against the same horizontal
threshold while their error-contraction curves fall on opposite sides.

\begin{proposition}[Bounded frontier classification; DD-C-0099 and DD-C-0100]
The frozen 177-scenario registry contains 126 strict-compression-dominated
curves, 16 strict-aggregation-dominated curves, and 35 all-neutral curves. The
stored error ratios reproduce the theorem's sign in every registered row.
\end{proposition}

\input{figures/registry-classification.tex}
\input{tables/registry-counts.tex}

The names describe the frozen curves. ``Compression dominated'' means residual
error did not contract fast enough relative to rescue at each applicable step;
``aggregation dominated'' means it contracted faster; ``all neutral'' means the
frontier held with equality. The registry is a systematic stress test across
named finite channel families and parameter values, not a probability sample of
real organizations.

\begin{proposition}[Minimal registered witnesses; DD-C-0100]
Under the frozen lexicographic ordering, the registry contains minimal witnesses
for equal-baseline opposite signs, equal-accuracy recovery differences, a
shared-discovery-paradox configuration, and consensus dominance. Their exact
values appear in \cref{tab:witnesses}.
\end{proposition}

\input{tables/minimal-witnesses.tex}

\begin{proposition}[Preserved bounded null; DD-C-0103]
No registered curve is mixed: none crosses from aggregation dominated to
compression dominated, or conversely, over its recorded sharing steps.
\end{proposition}

\Boundary{The zero mixed count is a verified bounded negative result. It does
not imply that arbitrary channels have monotone sharing curves. A mixed curve
outside the registry would not contradict the theorem; it would simply place
different steps on different sides of the exact frontier.}

This distinction illustrates the paper's evidence discipline. The analytic
criterion applies wherever its assumptions hold. The class counts apply only to
the frozen registry. The absence of a class is retained because negative results
inform the next search, but it is not converted into a universal statement.

\section{Centralized action-budget recovery}

Pooling need not be evaluated at one common action. If a planner can assign
several actions after observing pooled evidence, the top-$L$ posterior coverage
$V_L$ is nondecreasing in $L$. At full candidate capacity it is one. The direct
private portfolio cannot exceed one, giving a general recovery statement.

\begin{theorem}[Full-capacity recovery; DD-C-0098]
For every registered finite channel with $M$ candidates,
\[
 V_M=1\geq P_N.
\]
Hence a finite minimum recovery budget $L^*\leq M$ exists. Moreover,
$L^*=1$ if and only if $C_N=V_1\geq P_N$.
\end{theorem}

\begin{proof}
The posterior masses sum to one, so choosing all $M$ candidates covers the state
with probability one. Monotonicity of ordered partial sums implies existence of
the first $L$ reaching $P_N$. The last statement is the definition at $L=1$.
\end{proof}

The theorem is an existence result under centralized authority, not a claim
that $M$ decentralized agents will choose distinct actions. It also does not say
that pooling is costless: an organization may lack $M$ actions or may value
actions for other tasks. It identifies the precise capacity question that must
be answered after pooling.

\begin{proposition}[Bounded recovery census; DD-C-0101 and DD-C-0102]
In the frozen 177-scenario registry, recovery budgets $L^*=1,2,3,4$ occur in
$51,55,64,7$ scenarios respectively. Every registered scenario satisfies the
full-capacity theorem and the exact stored recovery characterization.
\end{proposition}

The distribution demonstrates why a binary recommendation---share or do not
share---is usually underspecified. For 51 scenarios, one centralized action
after pooling already matches the direct private baseline. For 126, at least two
actions are required, and seven need all four. The relevant design variable is
the pair consisting of information architecture and post-sharing action budget.

The distinction also helps compare centralization with communication. A team
can share signals without granting a planner binding authority; it can grant a
planner an action budget without pooling all raw signals; and it can retain
private rescue capacity after producing a common recommendation. These designs
occupy different points in the space summarized by \cref{fig:architecture}.

\section{Coordination-free positive sharing}

We now turn from nonstrategic rescue to a Bayesian game. There are two agents
and two target labels. The state is equally likely. Each clue is correct with
probability $p>1/2$. A hidden branch is common with probability $\rho$ and
independent with probability $1-\rho$. In the common branch the clue-generation
shock is shared; in the independent branch it is not. Agents do not observe the
realized branch. After actions, discovery pays one if at least one chosen label
is correct, split equally among agents choosing that correct label.

Let $t=2p-1$ and
\[
 A=t^2+\rho(1-t^2).
\]
The private selection is the registered anonymous, label-equivariant Bayesian
Nash equilibrium. The shared selection uses identical mixing as a function of
the common posterior only. These restrictions make the compared objects exact
and reproducible, but they are selection assumptions.

\begin{theorem}[Selected equilibrium formulas; DD-C-0104 and DD-C-0105]
In the private selection, the probability $r$ of following one's clue is
\[
 r^*=\begin{cases}
 1,&A\leq3t,\\[2pt]
 \frac12+\frac{3t}{2A},&A>3t.
 \end{cases}
\]
After sharing, agreement produces posterior correctness
\[
 u=\frac12+\frac{t}{1+A}.
\]
The selected probability $x$ of following the agreed label is
\[
 x^*=\begin{cases}
 1,&u\geq2/3,\\
 3u-1,&u<2/3,
 \end{cases}
\]
while disagreement uses the symmetric probability $1/2$.
\end{theorem}

The formulas follow from indifference and boundary conditions in the two-action
game. They do not assume that sharing reveals which dependence branch generated
the clues. Agreement is informative about the state and about the likelihood of
common generation; it does not disclose the realized common/independent branch.

\input{tables/equilibrium-formulas.tex}

\begin{theorem}[Strict selected sharing gain at $p=3/5$; DD-C-0106]
Let $p=3/5$. Shared selected discovery is strictly greater than private selected
discovery exactly for
\[
 \rho\in(\rho^*,1),\qquad
 \rho^*=\frac{5\sqrt{73}-17}{48}.
\]
Equality holds at $\rho^*$ and at $1$. The certified isolating interval is
$2679/5000<\rho^*<67/125$.
\end{theorem}

\begin{proof}[Proof sketch]
Substitute $t=1/5$ into the regime formulas. The shared rule changes regime at
$\rho=1/6$ and the private rule at $\rho=7/12$. On each interval the discovery
difference is rational in $\rho$. Clearing positive denominators yields the
certified algebraic equality with its unique interior root
$(5\sqrt{73}-17)/48$. Exact sign checks on the isolated intervals give a strict
gain between that root and one, with equality restored at perfect dependence.
The immutable certificate supplies the symbolic factors and rational isolating
interval; no floating-point root is used in the theorem.
\end{proof}

\begin{corollary}[Selected payoff gain; DD-C-0107]
At $p=3/5$, the same open interval strictly improves expected payoff per agent
under the registered selections.
\end{corollary}

\input{figures/dependence-discovery.tex}
\input{tables/threshold-gap.tex}

The mechanism is not ``correlation is good.'' At low dependence, private clues
provide useful diversity and sharing induces avoidable crowding. At intermediate
dependence, the private selected response itself becomes anti-crowding, while
agreement after sharing is informative enough to support a better selected
balance. At perfect dependence, sharing adds no information relative to the
identical private clues, and the selected values meet again. Dependence affects
both posterior aggregation and strategic duplication.

The bounded $7\times6$ registry contains 42 exact $(p,\rho)$ cells: six positive,
18 negative, and 18 neutral comparisons (DD-C-0108). This is a complete count of
the registered grid, not a measure of the interval's size and not evidence about
empirical frequencies.

\section{Equilibrium selection and implementation failure}

The positive theorem compares two named equilibria. It does not state that
sharing improves every equilibrium or even the best or worst equilibrium in the
full correspondence. This qualification is mathematical, not rhetorical.

\begin{theorem}[Selection failure; DD-C-0109]
For every $\rho$ in the registered binary model, private play admits pure
equilibria in which the two agents choose opposite constant targets. These
equilibria attain discovery one. After sharing, ownership-aware disagreement
strategies can assign different targets when clues disagree and lie outside the
posterior-only identical-mixing selection. Therefore the strict interval in
\cref{eq:positive-interval} is not an every-equilibrium improvement result.
\end{theorem}

\begin{proof}[Argument]
With opposite constants, exactly one agent selects the true binary target in
every state. A unilateral deviation can only duplicate the other target in one
state or exchange which state is covered, so it does not yield a strict payoff
gain under the registered split-prize game. For shared disagreement histories,
the agents' ownership of the two private clues provides a role variable. Mapping
those roles to opposite actions covers both targets, but the mapping is not a
function solely of the common posterior. These constructions are checked
symbolically in the DD-022 proof record.
\end{proof}

\input{figures/selection-map.tex}

Equilibrium selection is a substantive institutional primitive. Anonymous
label-equivariant restrictions rule out fixed label roles. Posterior-only shared
strategies rule out conditioning on who observed which clue. Identical mixing
rules out asymmetric role assignment. Each restriction may be appropriate for
an application, but none follows merely from ``the agents share information.''
Classical equilibrium-selection theory similarly emphasizes that a game can
admit many self-consistent predictions \citep{HarsanyiSelten1988}.

\begin{theorem}[Centralized implementation gap; DD-C-0110]
At $p=3/5$, a centralized top-two planner attains $V_2=1$. Its gap above the
selected shared equilibrium is
\[
 \frac{7+3\rho}{25}\quad\text{in the low shared regime},
 \qquad
 \frac{4+3\rho}{13+12\rho}\quad\text{in the high shared regime},
\]
and is strictly positive.
\end{theorem}

Centralized top-two is an authority benchmark: it assigns distinct targets. It
is not an equilibrium generated by information sharing alone. Opposite constant
private equilibria also reach one, but for a different reason and without using
the clues. Reporting only the common value would hide the difference between
binding action assignment and decentralized strategic coordination.

Communication can also be strategic. Cheap-talk models show that what is sent
depends on preferences and incentives \citep{CrawfordSobel1982}; jury and voting
models show that information aggregation depends on strategic behavior
\citep{AustenSmithBanks1996,LevyRazin2015}. The current model holds truthful clue
sharing fixed and studies the action game that follows. It therefore isolates
one implementation boundary but does not solve strategic disclosure.

\Boundary{The positive sharing theorem, the selection failure, and the planner
gap are jointly necessary for interpretation. Dropping the selection qualifier
would change the theorem. Dropping the planner label would conflate information
with authority.}

\section{Design implications and limitations}

The results support a diagnostic sequence rather than a universal prescription.
First, specify the discovery objective: top-one accuracy, coverage by a portfolio,
or expected payoff can rank architectures differently. Second, measure signal
geometry through posterior coverage or residual error, not only marginal
accuracy. Third, state how many independent actions survive pooling. Fourth,
identify who can assign actions and which equilibrium or behavioral rule is being
compared. Finally, preserve null and negative findings within their registered
scope.

For centralized teams, the action-budget profile is the natural planning object.
If $V_1<P_N$ but $V_2\geq P_N$, the informational case for sharing may be sound
while a one-action implementation is not. The design response could be to reserve
a second action, maintain a private red team, or make the pooled output a
shortlist rather than a single recommendation. The theorem does not price these
options; it reveals where such pricing enters.

For decentralized systems, role design can matter as much as disclosure. Agent
identifiers, clue ownership, randomized conventions, and assignment authority
change the implementable strategy space. Information sharing can improve one
symmetric selection while an asymmetric or ownership-aware equilibrium performs
better. A deployment claim should therefore name its selection mechanism rather
than report ``the equilibrium.''

Social-learning models explain how repeated observation can create herding,
cascades, and overweighting of common sources
\citep{Banerjee1992,BikhchandaniEtAl1992,DeMarzoEtAl2003}. The current finite
models share the concern that correlation and duplication are easy to misread,
but they do not estimate a dynamic learning process. Public information can also
have coordination benefits or costs in macroeconomic games
\citep{MorrisShin2002,CornandHeinemann2008}; our discovery objective and rescue
portfolio produce a different, explicitly action-budgeted frontier.

Information design asks how a designer should choose signals or recommendations
\citep{KamenicaGentzkow2011,BergemannMorris2016}. We mostly take the registered
channels as given. The frontier could become a design constraint---choose a
pooled signal whose residual error contracts beyond the rescue threshold---but
optimizing over all feasible experiments is outside the verified claims. Team
theory likewise asks how information should be allocated under decentralized
decision rules \citep{Radner1962}. Our contribution is a small exact bridge from
pooled coverage to discovery portfolios and selection boundaries.

Several limitations are structural. Rescue actions are independent in the
nonstrategic identity; correlated rescue would require their joint failure
probability. The finite channel registries do not span arbitrary experiments.
The strategic model is binary, two-agent, and uses a specific split-prize payoff.
Sharing is truthful and costless. No agent can acquire additional information,
and no communication network is modeled. The planner values discovery only and
can bind actions. The strategic positive interval fixes $p=3/5$ and two named
equilibrium selections. No welfare claim is made beyond the registered discovery
and payoff objects.

The empirical boundary is equally important. No participants were recruited,
no human or real organizational data were collected, and no experiment was run.
The displayed counts are exact bounded enumerations of synthetic model inputs.
They should motivate experimental contrasts, not be described as observations.

\input{figures/evidence-authority-map.tex}
\input{tables/claim-evidence-map.tex}

The evidence architecture makes extension possible. A new channel family could
be registered and classified by its contraction ratios. A richer strategic
study could expand the equilibrium correspondence or introduce an explicit
selection institution. An empirical study could preregister sharing and action-
budget treatments. None of those future directions is silently included here.

\section{Conclusion}

Information sharing improves decentralized discovery when its aggregation gain
is large enough to replace the independent rescue capacity it removes and when
the relevant decentralized behavior actually implements that gain. The first
condition is captured exactly by the residual-error frontier
$e_{s+1}/e_s<1-q$. The second requires an equilibrium or institutional account.

Finite channel examples show why accuracy alone cannot answer the question.
Equal one-person accuracy and equal private discovery can coexist with sharply
different pooled profiles, recovery budgets, and sharing directions. Full
centralized action capacity always recovers the private baseline, but the
required budget is part of the design, not a free consequence of communication.

The strategic model supplies a strict positive interval without planner action
assignment, but it simultaneously supplies the boundary: the result belongs to
named equilibrium selections. Alternative private and ownership-aware strategies
and the centralized top-two benchmark prevent an every-equilibrium or pure
information interpretation. The useful conclusion is therefore conditional and
operational. Share when pooled residual error clears the rescue threshold, retain
enough action capacity, and state how diverse actions will be selected.

\appendix
\section{Proof details for the sharing identities}

This appendix records algebra used by the synthesis; the scientific ownership
remains with DD-020 and DD-021. Let $F_s$ denote failure of the pooled block and
$R_i$ failure of private rescue action $i$. Under the registered protocol,
$\Prb(F_s)=1-C_s$ and the $N-s$ rescue failures are independent with probability
$1-q$. Therefore
\[
 \Prb(F_s\cap R_1\cap\cdots\cap R_{N-s})=(1-C_s)(1-q)^{N-s}.
\]
Taking one minus this probability proves \cref{eq:incremental-value}. At the next
step, one fewer rescue action remains. Subtraction gives
\begin{align*}
G_{s+1}-G_s
&=(1-C_s)(1-q)^{N-s}-(1-C_{s+1})(1-q)^{N-s-1}\\
&=(1-q)^{N-s-1}\left[(1-q)e_s-e_{s+1}\right].
\end{align*}
The factor outside the brackets is nonnegative and is positive away from the
degenerate $q=1$ boundary. If $e_s>0$, division by $e_s$ produces the contraction
ratio. Notice that $C_{s+1}\geq C_s$ alone is not enough. The absolute gain must
be large enough relative to $q e_s$, the rescue value applied to the current
pooled miss probability.

Two boundary cases deserve explicit labels. If $e_s=0$, the current pooled block
already discovers surely; the ratio is undefined but the undivided identity
remains valid. If $q=1$, any remaining rescue action guarantees discovery, so
absorbing the last perfect rescuer cannot improve the portfolio. These cases do
not affect the registered theorem rows but prevent careless division.

\section{Canonical exact records}

For auditability, the principal frozen profiles are restated here. DD-019 records
\begin{align*}
\text{noisy point: }&(7/12,43/54,25/27),&P_3&=7/8,&L^*&=3,\\
\text{noisy shortlist: }&(35/64,79/96,539/576),&P_3&=387/512,&L^*&=2,\\
\text{guaranteed shortlist: }&(17/18,1,1),&P_3&=7/8,&L^*&=1,\\
\text{exclusion: }&(16/27,26/27,1),&P_3&=19/27,&L^*&=2,\\
\text{confidence point: }&(295/384,175/192,31/32),&P_3&=485/512,&L^*&=3.
\end{align*}
The associated DD-020 paths are respectively
\begin{align*}
&(7/8,3/4,7/12),\quad (387/512,11/16,35/64),\\
&(7/8,11/12,17/18),\quad (19/27,17/27,16/27),\\
&(485/512,113/128,295/384).
\end{align*}
These are exact source values, not numbers reconstructed from the plotted lines.

At $p=3/5$, DD-022 records the selected discovery comparisons at
$\rho\in\{0,1/6,1/4,1/2,7/12,3/4,1\}$. The private selected sequence is
$21/25,4/5,39/50,18/25,7/10,27/38,18/25$; the shared selected sequence is
$18/25,7/10,45/64,27/38,57/80,63/88,18/25$. The source CSV distributed with
\cref{fig:strategic} includes these cells and the centralized value one.

\section{Protocol-level derivations and interpretation checks}

This appendix makes explicit the sequence of objects that can otherwise be
compressed into the phrase ``sharing improves discovery.'' It introduces no new
claim; it is an editorial derivation and interpretation audit of DD-019 through
DD-022.

\subsection*{From a channel to an action-budget profile}

Fix a prior and a finite signal history $h$. Bayes' rule produces posterior
masses $\pi_j(h)$ over candidates. Sort them as
$\pi_{(1)}(h)\geq\cdots\geq\pi_{(M)}(h)$. Conditional on $h$, a centralized
planner with $L$ distinct actions covers the correct candidate with probability
$\sum_{j=1}^L\pi_{(j)}(h)$. Averaging over histories produces $V_L$. This
calculation uses the complete posterior vector. Keeping only
$\max_j\pi_j(h)$ would determine $V_1$ but discard the marginal value of actions
two through $M$.

That lost information explains the equal-accuracy example. Accuracy constrains
the expected success of a registered top action. It does not determine whether
the posterior error is concentrated on one runner-up or spread over several
candidates. A guaranteed shortlist can put essentially all mass into a known
small set even when its top-label correctness is only one half. A noisy point can
leave substantial mass outside the first two ranks. Because discovery is a
coverage objective, the ordering of the remaining masses matters directly.

The profile is centralized by construction. A decentralized team could attain
the same set of actions if it had an implementation device: binding assignments,
public roles, or a supported equilibrium that maps agents to distinct ranks.
Absent such a device, $V_L$ remains a benchmark. This label prevents a common
category error in which a planner's ordered posterior sum is reported as the
automatic consequence of agents observing the same evidence.

\subsection*{From a profile to an incremental-sharing path}

The registered incremental protocol chooses a block size $s$. Its pooled block
has a specified coverage $C_s$; the remaining agents act as independent rescue
attempts. The comparison between $s$ and $s+1$ therefore changes both the pooled
history and the number of rescue attempts. Holding the latter fixed would answer
a different question: the marginal value of an additional signal with no
capacity cost. Holding the pooled coverage fixed would answer the marginal value
of an independent attempt. The sharing frontier is the net comparison.

The failure representation is useful because discovery is a union event. The
current architecture fails only if the pooled block fails and every rescue
attempt fails. The next architecture may have a smaller pooled failure
probability, but it also contains one fewer multiplicative rescue factor. The
break-even equation
\[
 e_{s+1}=(1-q)e_s
\]
says that the pooled block must remove the same share of its residual error as a
private attempt would have removed. A strict inequality determines the sign
without requiring the absolute level of $G_s$.

The ratio formulation is scale-free but not assumption-free. If rescue attempts
are correlated, $(1-q)^{N-s}$ must be replaced by their joint conditional failure
probability. If rescue quality depends on the pooled history, the common $q$
must be indexed by that history. If pooled agents retain individual actions, the
capacity transition is no longer one-for-one. Each extension is feasible, but
none is silently covered by DD-C-0097.

\subsection*{From a theorem to a bounded classification}

The analytic frontier gives a predicate for each applicable step. DD-021 then
applies that predicate to a versioned registry. A curve is called aggregation
dominated when each strict step lies below the rescue threshold, compression
dominated when each strict step lies above it, all-neutral when equality holds
throughout, and mixed when different steps have different strict signs. The
class labels are summaries of exact records, not primitives in the theorem.

The distinction between proof and census is important. A test that recomputes
all 177 rows can detect implementation drift and show that the theorem agrees
with those fixtures. It cannot prove the formula for unenumerated parameters.
Conversely, the algebraic proof does not imply that the registry contains a
mixed witness. Keeping the analytic and bounded layers separate is what allows
the zero mixed count to remain a useful negative result without becoming an
unsupported universal monotonicity claim.

Minimal witnesses are also registry-relative. The word ``minimal'' refers to
the frozen lexicographic ordering over registered parameters. It does not mean
minimal among every mathematically possible channel or in description length.
This qualifier is carried into \cref{tab:witnesses} and the generated asset note.

\subsection*{From private clues to selected equilibria}

The DD-022 comparison begins with a hidden mixture over source dependence. The
parameter $\rho$ is the prior probability of the common-source branch. Observing
two agreeing clues raises confidence in their label and changes beliefs about
which branch was likely, but it does not reveal the branch realization. A
strategy that conditions on ``the clues were common'' would therefore use
information unavailable to the agents.

Before sharing, each agent sees one clue and not the other's. Anonymous
label-equivariance requires the same response after relabeling targets. The
selected symmetric equilibrium can then be summarized by a clue-following
probability $r$. The statistic $A=t^2+\rho(1-t^2)$ captures the unconditional
alignment created by clue accuracy and source dependence. At $A=3t$, the
boundary solution gives way to interior anti-crowding. The exact piecewise
formula in \cref{tab:equilibrium-formulas} is the registered selection.

After sharing, the information histories are agreement on a label or
disagreement. At agreement, $u$ is the posterior probability that the agreed
label is correct. Identical posterior-only mixing is summarized by $x$. At
disagreement the posterior over targets is one half, so the selected identical
mix is one half. This last step is where ownership information is deliberately
discarded: although the common posterior is symmetric, agent one and agent two
can still know which private clue each originally owned.

The positive interval compares the discovery induced by these two selections.
It is meaningful because both are exact Bayesian Nash equilibria under their
registered restrictions. It is limited because equilibrium existence does not
select them from all alternatives. An opposite constant-target profile ignores
the signals but covers the binary state space. An ownership-aware rule can use
agent identity to split actions after disagreement. These constructions do not
invalidate the selected interval; they invalidate a stronger interpretation of
it.

\subsection*{Three meanings of discovery one}

The value one appears in three places that must not be collapsed. First, a
centralized planner with two actions covers both binary targets by binding
assignment. Second, opposite constant-target private equilibria cover both
targets through a fixed decentralized convention. Third, an ownership-aware
shared rule can cover both targets on disagreement histories while behaving
differently on agreement. The same discovery number masks different evidence
use, authority, and off-path behavior.

For organizational design, this means that performance tables need an authority
column. A benchmark labeled ``centralized top-two'' is evidence about attainable
coverage under control, not about spontaneous coordination. A row labeled
``selected shared equilibrium'' is evidence about one decentralized behavioral
rule. A row labeled ``alternative equilibrium'' is evidence about multiplicity.
The generated selection map and evidence-authority map enforce those labels
visually.

\subsection*{Reading the canonical plot}

In \cref{fig:strategic}, the dashed direct-private curve is not the private
selected equilibrium after the private anti-crowding boundary. The selected
private curve initially follows direct clue use, then changes when mixing becomes
optimal. The selected shared curve changes formula at its own boundary $1/6$.
Its intersection with the private selected curve at $\rho^*$ is algebraic, not a
linear interpolation of plotted cells. The second equality at $\rho=1$ reflects
the fact that perfectly common clues contain no additional cross-agent evidence
when shared.

The connected points in the figure are a display of registered exact cells. The
theorem between them comes from piecewise symbolic formulas and a certified root
isolation. The decimal marker is only a visual aid. The exact expression and
rational bracket control every sign claim.

\subsection*{Interpretation checklist}

For each proposed use of the results, the following questions identify the
relevant row of the evidence map:
\begin{enumerate}[leftmargin=2em]
\item Is the outcome top-choice accuracy or coverage by at least one action?
\item Does sharing reduce the number of independent actions, and by how much?
\item Are remaining rescue attempts independent conditional on pooled failure?
\item Is the displayed action budget feasible and centrally assignable?
\item If actions are decentralized, which equilibrium selection or role system
      maps shared evidence to distinct actions?
\item Is a reported count an analytic theorem, a bounded exact census, or a
      preserved null inside a registered search space?
\item Does the protocol reveal only the pooled clues, or also an unavailable
      latent source branch?
\item Are claims about model-generated values kept separate from claims about
      people, organizations, or deployed multi-agent systems?
\end{enumerate}
An application that cannot answer these questions has not yet specified the
comparison made by this paper.

\section{Evidence, provenance, and reproducibility}

The generator resolves all 22 claim IDs against the claim ledger, verifies the
ten source-output hashes against immutable run manifests, writes exact CSV data
for every figure, and writes TeX tables and figures with run IDs, claim IDs, the
generator name, and input checksum prefixes. It then builds the PDF twice under
a fixed source epoch and requires byte-identical hashes. An independent paper
audit rechecks the source contracts without importing the generator and performs
deliberate corruption tests on copied metadata.

The manuscript makes no new claim record and no new study or run. DD-019 owns
the signal-geometry results, DD-020 the incremental identity and counterchannel,
DD-021 the general frontier and recovery registry, and DD-022 the strategic
equilibrium results. Editorial synthesis does not change those ownership lines.
The citation database is copied into the generated bundle at build time so the
compiled bibliography is pinned to the paper artifact.

\section{Literature boundary}

The adjacent literatures establish why narrow contribution language is needed.
Blackwell comparison concerns informativeness across decision problems
\citep{Blackwell1953}. Team decision theory concerns decentralized information
allocation \citep{Radner1962}. Herding and social-learning models concern the
endogenous informational content of observed behavior
\citep{Banerjee1992,BikhchandaniEtAl1992,AcemogluEtAl2011}. Strategic
communication concerns incentive-compatible messages \citep{CrawfordSobel1982}.
Information design concerns signal or recommendation choice
\citep{KamenicaGentzkow2011,BergemannMorris2016}. Equilibrium selection concerns
which equilibrium is predicted when several exist \citep{HarsanyiSelten1988}.

The present synthesis composes a particular portfolio objective, rescue
technology, coverage profile, and selected action game. That composition may be
useful without supporting a claim that no related frontier, anti-crowding
mechanism, or selection caveat exists elsewhere. The accompanying literature
files record stable identifiers and the claim-by-claim relationship.

\bibliographystyle{plainnat}
\bibliography{generated/references}
\end{document}
