\documentclass[11pt]{article}

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsthm,mathtools}
\IfFileExists{newtxtext.sty}{\usepackage{newtxtext,newtxmath}}{\usepackage{mathptmx}\usepackage{amssymb}}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{booktabs,tabularx,array}
\usepackage{float}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,calc}
\usepackage{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\definecolor{planner}{HTML}{2A78D6}
\definecolor{private}{HTML}{087D26}
\definecolor{market}{HTML}{A76900}
\definecolor{consensus}{HTML}{B4476F}
\definecolor{inktwo}{HTML}{52514E}
\setstretch{1.035}
\setlength{\parskip}{0.25em}
\setlength{\parindent}{1.2em}
\setlength{\emergencystretch}{2em}
\Urlmuskip=0mu plus 1mu
\setlist{leftmargin=1.5em,itemsep=0.2em,topsep=0.3em}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\Prob}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Tteam}{T_N(M,p)}
\newcommand{\ArtifactNote}[1]{\par\begin{minipage}{.96\textwidth}\scriptsize\color{inktwo}#1\end{minipage}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{\textbf{Three Results in Distributed Discovery}\\[0.35em]
\large Roles, Disclosure, and Source Dependence}
\author{Yohei Nakajima\\{\normalsize Untapped Capital}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Collective search depends on more than the quality of a shared ranking. It also
depends on who is assigned to test what, which strategic outcome is selected, and
whether nominally separate reports arise from distinct sources. We synthesize
three finite results around those margins. First, ex-ante role policies can improve
discovery without communication: at $(M,N,p)=(3,2,2/5)$ a hybrid policy attains
$7/10$, strictly above direct clue-following $16/25$, and a restricted family has
exact territorial--hybrid--direct thresholds. Second, in a complete deterministic
disclosure fixture, one Blackwell refinement lowers discovery under the declared
anonymous-symmetric selection from $5/9$ to $171/308$, even though every pure
equilibrium and the planner improve. An exact six-rule catalogue shows that this
known reversal survives only anonymous-symmetric selection among the audited
alternatives. Third, among 51 nonisomorphic latent-source
graphs with homogeneous accuracy, complete pairwise report moments yield a bounded
null. In a registered 839-network colored extension, however, two networks have
identical complete first/pairwise moments but discovery $3/4$ and $2/3$; average
agreement is also insufficient. We connect these results through a common
information--action framework and preserve their distinct evidence boundaries.
For the canonical private-team fixture, an alignment-preserving exact relaxation
also meets the direct-policy lower bound, proving direct clue-following globally
optimal without communication.
The paper makes no claim of a new field or universal law.
\end{abstract}

\noindent\textbf{Keywords:} collective search, team decision, information design,
source dependence, equilibrium selection, distributed discovery.\\
\textbf{Evidence note:} All displayed numerics and generated figures are derived
from checksum-validated immutable runs. Claim IDs refer to the public repository
ledger; exactness and independence are claim-specific.
\textbf{Publication status:} Synthesis note; not submitted, not peer reviewed,
and no DOI.

\section{Introduction}
% Claims: DD-C-0001, DD-C-0002, DD-C-0016, DD-C-0017
Many organizations use the language of ``the best answer'' even when their
operational task is to allocate several attempts. A research group chooses a
portfolio of experiments, a venture fund chooses investments, and a multi-agent
system chooses investigations or tool calls. In each case evidence ranks
candidates, but discovery depends on the union of actions rather than the quality
of a single recommendation. The Shared Discovery Paradox isolates this difference:
pooling improves the leading recommendation, yet a one-answer convention can
compress several actions into repetition and reduce discovery
\citep{Nakajima2026SharedDiscovery}.

The broader program calls this conversion from dispersed evidence into a finite
action portfolio \emph{distributed discovery}. The name is a working definition,
not a novelty or ownership claim. The phrase has other uses, and the component
questions belong to established literatures: Blackwell comparison and persuasion
for information, team theory for private common-payoff decisions, organizational
and scientific search for division of effort, and coverage games for strategic
action allocation \citep{Blackwell1953,MarschakRadner1972,KamenicaGentzkow2011,
March1991,Kitcher1990,Vetta2002}. The contribution here is to place three finite
results in one explicit architecture while retaining their separate scopes.

The first result concerns \emph{roles}. Agents commit to different mappings from
private clues to actions before seeing those clues and act without communication.
Direct clue-following is feasible but need not be optimal. A constant territory
can reserve a candidate while another agent remains responsive to evidence. This
mechanism is allocative: no new signal is created, and no report is pooled at
action time.

The second result concerns \emph{selection}. A public disclosure changes posterior
games played by autonomous searchers. More informative disclosure expands what a
planner can do, but a named equilibrium-selection rule can move toward a more
concentrated outcome. The finite reversal below is therefore related in spirit to
informational Braess effects, not to a failure of frontier monotonicity
\citep{AcemogluEtAl2018}. Its central qualifier is that all pure equilibria improve
for the same witness, and an exact catalogue shows that five alternative rules do
not reproduce that witness.

The third result concerns \emph{representation}. Correlated reports may come from
latent source networks. One scalar summary of agreement can hide discovery-
relevant structure. A homogeneous bounded class records where the complete
pairwise matrix did not fail; exact accuracy colors then produce nonisomorphic
networks with the same full pairwise object and different discovery. The positive
counterexamples and preserved negative search identify the perturbation that
breaks the earlier null.

These mechanisms should not be collapsed into a slogan that ``diversity is good''
or ``more information is bad.'' Roles change the feasible private policy class;
disclosure changes a posterior game and its selected equilibrium; source networks
change the joint evidence law. Our unifying statement is narrower: collective
discovery depends not only on what agents know, but on how roles are assigned, how
strategic outcomes are selected, and how source dependence is represented.

The remainder defines the common accounting and evidence discipline, presents the
three results, draws their limited joint implications, and states the unresolved
questions. The canonical upstream paper remains the concise source for the atomic
paradox and its strategic/scaling results. The Foundations note remains the source
for the general vocabulary. This paper is a results synthesis, not a replacement
for either.

\section{Framework and evidence discipline}
% Claims: DD-C-0002, DD-C-0011, DD-C-0016, DD-C-0018, DD-C-0019
\subsection{Information and action as separate objects}

An atomic discovery problem has a target $\theta\in\{1,\ldots,M\}$ and $N$
actions. If $S$ is the set of distinct tested labels, discovery is
$\mathbf 1\{\theta\in S\}$. An information architecture specifies which evidence
each decision maker observes. A protocol maps that information to a feasible
action vector. With budget $B$, information architecture $I$, and feasible
protocol class $\mathcal P_B(I)$, define
\[
G_B(\Pi;I)=\Prob_\Pi(\theta\in S),\qquad
V_B(I)=\sup_{\Pi\in\mathcal P_B(I)}G_B(\Pi;I).
\]
Protocol loss is $L_B(\Pi;I)=V_B(I)-G_B(\Pi;I)$, hence
\[
G_B(\Pi;I)=V_B(I)-L_B(\Pi;I).
\]
This is an accounting identity (DD-C-0002), not an efficiency theorem. Its use is
to prevent a comparison that changes information, authority, equilibrium
selection, and source dependence simultaneously from being assigned to only one
cause.

Frontier monotonicity requires emulation. If every protocol feasible under $I_1$
can be implemented under $I_2$ with the same outcome distribution, then
$V_B(I_2)\ge V_B(I_1)$ (DD-C-0016). The condition is stronger than saying that one
realized protocol sees more information. A richer public signal can change a game
and its selected outcome even when the planner frontier rises. This distinction is
the hinge between the disclosure result and Blackwell's decision-theoretic order
\citep{Blackwell1953,KamenicaGentzkow2011}.

\subsection{Three institutional margins}

The results occupy different cells of an information--authority matrix. A private
team chooses role policies ex ante, observes only local signals at action time,
and shares a common discovery objective. A disclosure game gives all agents a
public posterior but leaves actions strategic under an equal-split reward. A
source network changes how private reports are jointly generated while holding
the direct action rule fixed. These are not three algorithms for the same
feasible set; each changes a different primitive.

For the private team, ex-ante randomization cannot improve the finite common-payoff
optimum (DD-C-0018). Drawing contingent actions before signals produces a mixture
over deterministic profiles, and expected discovery is a convex combination of
their values. This is a team-decision sufficiency result, not purification of a
strategic mixed equilibrium \citep{MarschakRadner1972}.

A pooled planner provides an important but carefully scoped comparator. It
observes every private report and can apply any fixed role policy to reproduce the
team's action vector. Conditional on the reports, an eight-label top-posterior
portfolio weakly dominates any emulated multiset. Thus direct clue-following is a
lower bound and the pooled frontier is an upper bound under matched physical
actions and objective (DD-C-0019). The comparison crosses information and
assignment margins; it is a valid feasible-set bound, not an attainable private
policy.

\subsection{Claim-level evidence}

The numerical and mathematical objects below do not share one evidence status.
A theorem can be derived analytically and audited computationally. A finite
enumeration can be exact without supporting an all-parameter theorem. A selected
equilibrium reversal can be verified while remaining selection-dependent. A
failed exhaustive search over a declared finite class is a bounded null, not a
general sufficiency statement. Table~\ref{tab:evidence} makes these differences
visible.

\input{generated/evidence-status-table.tex}

Every computational statement traces to a passing immutable run with a frozen
configuration, clean source commit, environment, exact or floating arithmetic
basis, termination condition, output checksums, and validation flags. Independent
reproduction requires a materially different representation or evaluator, not a
second invocation of the same code. Corruption tests establish that certificate
checkers actually reject altered evidence. These practices do not replace proof
or peer review; they make the boundary of each claim inspectable.

\section{Private roles without communication}
% Claims: DD-C-0018, DD-C-0019, DD-C-0020, DD-C-0021, DD-C-0022, DD-C-0023, DD-C-0024, DD-C-0025, DD-C-0026, DD-C-0027, DD-C-0028, DD-C-0037, DD-C-0038
\subsection{The zero-communication team problem}

The target is uniform on $M$ labels. Agent $i$ receives clue $X_i$ with
\[
\Prob(X_i=\theta\mid\theta)=p,
\qquad
\Prob(X_i=x\ne\theta\mid\theta)=q=\frac{1-p}{M-1},
\]
independently conditional on $\theta$. Before clues are realized, the team commits
to deterministic role policies $f_i:\{1,\ldots,M\}\to\{1,\ldots,M\}$. Afterward
agent $i$ searches $f_i(X_i)$ without communication. The team frontier is
\[
T_N(M,p)=\max_{f_1,\ldots,f_N}
\Prob\{\theta\in\{f_1(X_1),\ldots,f_N(X_N)\}\}.
\]

Direct clue-following uses $f_i(x)=x$. Its value is
$1-(1-p)^N$. A territorial policy ignores clues and reserves a fixed label.
Hybrid policies combine both: one role can protect territory while another
redirects only selected signals. The objective rewards coverage, so sacrificing
some action-level accuracy can improve union success.

For a fixed profile, let $s_i(t)=\Prob(f_i(X_i)=t\mid\theta=t)$. Conditional
independence yields the exact factorization
\[
G(f_1,\ldots,f_N)=\frac1M\sum_{t=1}^M
\left[1-\prod_{i=1}^N(1-s_i(t))\right].
\]
This evaluator is separate from the direct target/signal enumeration used to
check winners in the finite grid.

\subsection{An exact role counterexample}

At $M=3$, $N=2$, and $p=2/5$, direct clue-following gives
\[
D(p)=1-(1-p)^2=2p-p^2=\frac{16}{25}.
\]
The hybrid profile with one constant policy $(0,0,0)$ and one rerouting policy
$(1,1,2)$ gives $7/10$. Exhaustive enumeration of all agent-symmetric policy
profiles proves this is the unrestricted deterministic optimum for the fixture;
raw direct enumeration and a later signature implementation reproduce it
(DD-C-0021, DD-C-0024). The exact gain is $3/50$.

\input{generated/roles-figure.tex}

The counterexample has a transparent mechanism. The constant role guarantees an
attempt at label zero. The other role follows signals one and two but maps a zero
signal to one, avoiding predictable duplication with the territorial agent. It
does not show that one fixed territory is always best, that communication is
harmful, or that the same profile is optimal at canonical dimensions. It refutes
only the general claim that every optimal private team follows its clue directly.

\subsection{A restricted phase theorem}

For $N=2$ and $M\ge3$, compare three families: two direct policies; two distinct
constant territories; and the one-reroute hybrid above. Their values are
\[
D(p)=2p-p^2,\qquad R_M=\frac2M,
\qquad H_M(p)=\frac{1+(M-2)p}{M-1}.
\]
Exact factorization of pairwise differences gives the thresholds
$p=1/M$ and $p=1/(M-1)$ (DD-C-0026). Territorial is best below $1/M$,
the hybrid is best between the thresholds, and direct is best above
$1/(M-1)$, with adjacent ties at the boundaries. This is a theorem within the
three named families for every $M\ge3$.

The restriction matters. A complete signature-polynomial census certifies that
the same hybrid-then-direct envelope is unrestricted over the continuous
informative interval $[1/M,1]$ for $M=3,4,5$ (DD-C-0027). The computation checks
438,734 feasible signature multisets with exact quadratic nonnegativity at
endpoints and interior vertices. It does not prove the envelope for all $M$.

Nor does the informative classification extend to every $p$. At $p=0$, exact
unrestricted optima are $11/12$ for $M=3$ and $2/3$ for $M=4$, strictly above the
three-family benchmarks $2/3$ and $1/2$ (DD-C-0028). These anti-informative
counterexamples show why a phase diagram needs an explicit parameter domain.

\subsection{Lossless policy signatures}

Raw policies number $M^M$ per agent. A policy can nevertheless be compressed
without changing any fixed-profile value. For target $t$, let $c_i(t)$ be the
number of signals mapped to $t$, and let $d_i(t)$ indicate whether signal $t$ is a
fixed point. Then
\[
s_i(t)=q c_i(t)+(p-q)d_i(t).
\]
The targetwise pairs $(c_i(t),d_i(t))$ therefore determine the full conditional
success vector and every profile objective (DD-C-0023).

Feasibility also has an exact characterization. Remove fixed rows and define
residual incoming counts $r_t=c_t-d_t$. A duplicated-column bipartite matching
exists exactly when local count conditions and the singleton residual Hall bounds
hold. A matching implementation reconstructs policies, while a separate closed-
form implementation audits feasibility. The signature representation independently
reproduces all 21 prior tiny optima and their raw-policy tie counts (DD-C-0024).

The compression does not eliminate the canonical difficulty. At $M=16$ there
are 148,348,284,928 feasible labeled signatures and 5,806 individual target-label
orbits. Eight-agent multisets before a global target quotient form an 85-digit
state count (DD-C-0025). Canonicalizing each agent separately loses relative target
alignment, which enters the product of failure probabilities. The barrier is not
a proof that exact optimization is impossible; it identifies what a valid next
quotient or relaxation must preserve.

\subsection{The exact canonical optimum}

For $(M,N,p)=(16,8,1/5)$, direct clue-following is feasible and has exact value
\[
1-(4/5)^8=\frac{325089}{390625}=0.83222784.
\]
The direct profile is an exact coordinate fixed point, and 17 additional declared
starts converged to the same value (DD-C-0022). Those searches alone were only
heuristic lower-bound evidence. The new proof instead retains the aligned vector
of incoming policy counts across all agents inside each target column. It lower-
bounds each local failure factor, exactly minimizes their product by column
resource, and then relaxes only cross-target feasibility while preserving the
globally necessary incoming-count total (DD-C-0037).

The resulting exact Bellman certificate assigns resource eight to each of the
sixteen targets and lower-bounds average failure by $(4/5)^8$. Hence
\[
\boxed{T_8(16,1/5)=\frac{325089}{390625}=0.83222784.}
\]
The upper bound meets the attainable direct value, proving global optimality for
deterministic teams. An ex-ante randomized policy is a mixture of deterministic
profiles, so the randomized optimum is identical (DD-C-0038). A separate verifier
checks every Bellman inequality and equality witness without optimizing and
rejects a corrupted final value. The former pooled upper endpoint remains a valid
organizational benchmark, but its exact gap has now been closed for this frozen
private-team problem.

\section{Information disclosure under strategic search}
% Claims: DD-C-0029, DD-C-0030, DD-C-0031, DD-C-0039, DD-C-0040, DD-C-0041
\subsection{A complete bounded fixture}

The disclosure result holds information and the physical action technology apart
from strategic selection. There are three target actions, two searchers, four
evidence states, and a fixed rational likelihood matrix. A deterministic public
disclosure policy is a set partition of the four evidence states, considered up
to message-label equivalence. The Bell number gives exactly 15 policies. Across
their messages the run evaluates 37 posterior games (DD-C-0029).

Agents compete for an equal-split prize: being the sole correct searcher receives
the whole prize, while duplicate correct searches split it. For each posterior
game, the computation exhausts labeled pure best responses and calculates the
anonymous symmetric equilibrium over its support. Cartesian products across
messages yield 256 global pure-equilibrium selections. This registry keeps the
correspondence separate from the named symmetric selection.

A disclosure $\pi'$ is more informative than $\pi$ when a deterministic garbling
maps messages of $\pi'$ to those of $\pi$. The complete partition lattice contains
45 strict refinement pairs. The planner's two-action value is the posterior mass
of its two highest-probability targets and therefore cannot fall under a refinement
when it can ignore the added message detail.

\subsection{The selected reversal}

The unique anonymous-symmetric reversal refines full pooling
$\{\{0,1,2,3\}\}$ into $\{\{0,1\},\{2,3\}\}$. Under pooling the selected discovery
is $5/9$. Under refinement it is the probability-weighted value $171/308$, lower
by $1/2772$ (DD-C-0030).

\input{generated/disclosure-figure.tex}

The qualification is central. Every pure-equilibrium discovery value rises from
$2/3$ to $3/4$ for this witness. The two-action planner value also rises from
$2/3$ to $3/4$. The refinement therefore does not make every equilibrium worse,
does not reduce the feasible information frontier, and does not show that public
information is intrinsically harmful. It changes the declared anonymous-symmetric
outcome in a direction that concentrates strategic search.

The witness is informational-Braess-like because information modifies equilibrium
behavior, while a coordinator could discard the added detail or choose a better
portfolio \citep{AcemogluEtAl2018}. It is also narrower than a Bayesian-persuasion
claim: the disclosure policy is not optimized over randomized experiments, the
sender objective is not solved, and the result does not characterize the concave
closure of value \citep{KamenicaGentzkow2011}.

\subsection{What the full refinement census says}

Across all 45 strict deterministic refinements, exactly one lowers the selected
anonymous-symmetric value, eight lower the worst pure-equilibrium value, none
lower the best pure-equilibrium value, and none lower the planner value
(DD-C-0031). Reporting only the selected witness would hide the favorable pure
correspondence; reporting only the best equilibrium would hide selection risk.
Both summaries are needed.

\subsection{Exact selection catalogue}

The same finite fixture admits an exact-potential characterization. For posterior
target probabilities $\mu$, define
\[
\Phi(a,b)=
\begin{cases}
3\mu_a/2,&a=b,\\
\mu_a+\mu_b,&a\ne b.
\end{cases}
\]
Every unilateral payoff difference equals the corresponding potential difference,
so every strict best-response path terminates (DD-C-0039). This permits an exact
catalogue beyond the initially declared anonymous-symmetric rule: best and worst
pure equilibria, uniform selection over global potential maximizers, and a process
that starts uniformly over the nine labeled profiles and chooses uniformly among
strict payoff-maximizing player/action moves. The planner remains a nonstrategic
comparator.

\input{generated/selection-robustness-table.tex}

For the known $P00\to P03$ witness, best pure, worst pure, potential-maximum,
best-response-basin, and planner values all rise from $2/3$ to $3/4$; only the
anonymous-symmetric value falls (DD-C-0040). Across all 45 refinements, the harmful
counts in table order are $1,0,8,2,2,0$. Thus selection risk is not confined to the
original rule---worst pure and the two dynamic/potential catalogues have other
harmful refinements---but the named witness itself is not robust across the five
alternatives (DD-C-0041). An independent implementation checks the posterior
games, potential identities, absorption Bellman equations, and all rule comparisons.

The census establishes completeness only for the declared four-state partition
lattice and likelihood fixture. Randomized disclosure was not studied. General
asymmetric mixed equilibria were not enumerated. Dynamic learning, equilibrium
refinement, and selection processes outside the audited strict-best-response rule
are outside the result. The catalogue resolves the planned robustness milestone;
expanding to randomized disclosure requires a separate solution concept and ADR.

\section{Correlated source networks}
% Claims: DD-C-0032, DD-C-0033, DD-C-0034, DD-C-0042, DD-C-0043, DD-C-0044
\subsection{From a copying scalar to provenance graphs}

Four searchers observe reports derived from one to three latent sources. A
bipartite graph says which source reports each searcher sees; no declared node is
isolated. Sources are independent conditional on a three-valued target and have
common accuracy $2/3$. A searcher combines adjacent source reports by a declared
plurality-winner-set rule with uniform tie sampling, then searches the resulting
label directly.

This model turns provenance into a graph rather than a single copying rate. Source
and searcher labels are nuisance symmetries, so graphs are equivalent under
independent relabeling of the two sides. Exhausting all labeled adjacencies and
canonicalizing them yields 1, 8, and 42 nonisomorphic graphs for one, two, and
three sources: 51 total (DD-C-0032). An independent orbit traversal reproduces
the counts and a pairwise nonisomorphism audit confirms the registry.

For each graph, exact enumeration over target and source-signal states produces
private discovery and report moments. The complete pairwise object includes every
searcher pair's one-hot report moment matrix, canonicalized only under searcher
relabeling. Two networks can have the same scalar mean agreement while differing
in this matrix, source overlap, and higher-order dependence.

\subsection{A bounded null for complete pairwise moments}

The 51-graph census contains ten complete pairwise-moment signatures that each
match two nonisomorphic graphs. All twenty graphs in those groups have equal
private discovery within their matched group. Thus no complete-pairwise-moment
counterexample exists in the configured class (DD-C-0033).

This is a bounded null, not a sufficiency theorem. It says the declared diagnostic
survived one complete exact test. A counterexample may appear with heterogeneous
source quality, more sources, different aggregation, more searchers, or another
target law. Conversely, the null matters operationally because it prevents a
failed search from being selectively forgotten and establishes a reproducible
baseline for the next perturbation.

\subsection{Heterogeneous accuracy breaks the null}

The registered perturbation carries each source accuracy as a color attached to
its adjacency row. Searchers may still be relabeled, while source relabeling moves
the exact color with the source. Four base profiles---equal $2/3$, modest
$\{1/2,2/3\}$, near-uninformative $\{1/3,2/3\}$, and strong
$\{1/3,5/6\}$---produce 41,612 valid labeled colored objects and 671 orbits. One
controlled three-color expansion adds 12,966 labeled objects and 168 orbits
(DD-C-0042). The equal profile reproduces all prior two/three-source values.

The complete-moment null fails already in the modest two-source profile. One
network attaches the $1/2$ source to one searcher and the $2/3$ source to all four;
the other reverses those degrees. They are not color-preserving isomorphic. Every
first action moment and all six $3\times3$ pairwise action-moment matrices match,
but private union discovery is $3/4$ versus $2/3$ (DD-C-0043).

\input{generated/heterogeneous-sources-table.tex}

Across the full 839-network registry, 163 complete-moment signatures match 485
networks and 111 matched groups contain different discovery values (DD-C-0044).
A separate implementation traverses the labeled colored orbits, directly checks
nonisomorphism, and reconstructs every 66-entry signature and discovery value.
Thus heterogeneity supplies an exact bounded counterexample, not a universal
impossibility theorem for all pairwise diagnostics.

\subsection{A scalar counterexample}

Average pair agreement is much weaker. Graphs \texttt{K2N4:00011110} and
\texttt{K2N4:01111111} both have mean pair agreement $3/4$, yet their exact private
discovery probabilities are $8/9$ and $31/36$, a difference of $1/36$
(DD-C-0034).

\input{generated/sources-figure.tex}

The two complete pairwise matrices differ, so the example refutes only the scalar
average. The full census has 22 graph pairs with matched average agreement and
different discovery. It also has 59 pairs with matched source Herfindahl--
Hirschman concentration and different discovery. Neither scalar is a sufficient
effective-channel statistic in this model.

The result does not imply that correlation is always harmful. Shared sources may
improve individual report quality or coordinate complementary actions in another
technology. Nor does it establish a universal effective sample size. Diagnostics
must be tied to the target law, aggregation rule, and action objective. Provenance
structure can matter beyond nominal report count, but which representation is
sufficient remains a model-specific question.

\section{Unified implications}
% Claims: DD-C-0002, DD-C-0016, DD-C-0021, DD-C-0030, DD-C-0040, DD-C-0041, DD-C-0033, DD-C-0034, DD-C-0043, DD-C-0044
The three results share an outcome---union discovery---but operate through
different causal and mathematical margins. It is useful to state the mapping
exactly:

\begin{center}
\small
\begin{tabularx}{\textwidth}{P{.15\textwidth}YYY}
\toprule
Study & Primitive changed & Mathematical object & Main boundary\\
\midrule
DD-001 roles & ex-ante policy assignment & common-payoff team frontier & canonical optimum exact; other parameters open\\
DD-002 disclosure & public signal partition & posterior game plus selection & known reversal survives one of six audited rules\\
DD-003 sources & joint evidence provenance & colored/bipartite source law & heterogeneity breaks the homogeneous pairwise null\\
\bottomrule
\end{tabularx}
\end{center}

First, allocation can substitute partly for communication. The DD-001 hybrid
improves coverage using differentiated role mappings while leaving every clue
private. The result does not say that information sharing lacks value; the exact
pooled planner remains an upper bound. It says assignment has an independent
margin that a direct symmetric protocol leaves unused.

Second, information and behavior must be separated. The DD-002 refinement
improves the planner and all pure equilibria for its witness while lowering one
selected symmetric outcome. Five audited alternatives do not reproduce that
witness, although other refinements are harmful under worst-pure, potential, and
best-response-basin summaries. A statement that ``information reduced discovery''
is incomplete without the selection procedure. Frontier monotonicity and realized
equilibrium performance can move in different directions.

Third, evidence diversity needs a representation. The homogeneous DD-003 census
preserves a bounded null for the full pairwise object, while exact source-accuracy
colors break it: pairwise observational equivalence can coexist with different
union discovery. A useful diagnostic must be validated against the downstream
action rule and perturbations of the generative law, not chosen solely because it
resembles a generic effective sample size.

These points support a layered design workflow. Declare the world and evidence
kernel; declare what each agent observes; declare the feasible role or assignment
class; declare rewards and equilibrium selection; declare how actions cover the
target space. Only then compare protocols. A change that bundles those layers may
still be useful, but its performance gap should not be given a single causal
label.

The scientific-search literature already studies richer dynamic divisions of
labor, communication networks, and experiment choice
\citep{March1991,Kitcher1990,Zollman2007,RzhetskyEtAl2015}. Submodular and adaptive
search add overlapping value and feedback \citep{NemhauserEtAl1978,
GolovinKrause2011}. Robotic coverage makes redundancy valuable for robustness
\citep{HazonKaminka2008}. The present finite models are best read as diagnostic
building blocks for those settings, not substitutes for them.

\section{Limitations}
% Claims: DD-C-0017, DD-C-0022, DD-C-0025, DD-C-0027, DD-C-0030, DD-C-0033
The first limitation is external validity. Every result is mathematical evidence
inside a declared model. No observational or experimental dataset establishes
that a real scientific group, company, market, or multi-agent system occupies the
same parameterization. Application mappings identify measurable primitives; they
do not transfer the ordering automatically.

Second, the role results are asymmetric in their strength. The policy-signature
identity and residual Hall characterization are general theorems for the finite
symmetric clue model. The three-family phase result is general only within its
named families. The unrestricted continuous classification is bounded to
$M=3,4,5$, and the anti-informative examples are two fixtures. The alignment
relaxation upper-bounds all symmetric-report parameters, but is not always tight;
its equality with direct clue-following proves the optimum only at the frozen
canonical fixture.

Third, the disclosure result fixes deterministic partitions of four evidence
states and six specified evaluations. It does not enumerate randomized disclosure,
general asymmetric mixed equilibria, or learning processes beyond the audited
strict-best-response basin. Because the known witness reverses under only one of
the six evaluations, the phrase ``harmful disclosure'' must always carry the
selection qualifier.

Fourth, the source-network model fixes source independence conditional on the
target, four searchers, two or three sources for the colored census, a finite
accuracy palette, and a particular plurality/tie rule. The complete pairwise
counterexample is exact only there. It does not cover continuous accuracies,
dependent sources, asymmetric target priors, larger graphs, or higher-order report
laws.

Fifth, exact enumeration is not equivalent to conceptual independence. The
repository requires distinct representations and direct state checks where
feasible, but all implementations share the frozen model. A misspecified
likelihood, objective, or selection definition could be reproduced perfectly.
Proof review and model criticism remain necessary.

Finally, the project makes no broad terminology or field novelty claim
(DD-C-0017). Team theory, information design, organizational search, epistemic
networks, and coverage games provide direct intellectual ancestry. The value of
the synthesis is an inspectable separation of information, roles, selection, and
source representation.

\section{Research agenda}
The immediate DD-001 proof task is complete: the first alignment-preserving
count-budget relaxation equals the direct lower bound canonically. The next
structural question is when that relaxation is tight. It matches all 21 prior tiny
fixtures but is strictly loose at the audited anti-informative
$(M,N,p)=(3,2,0)$ case. Stronger per-role cross-target consistency can be added as
a hierarchy only when a new question requires it.

For DD-002, the selection-robustness milestone is complete. Six fully specified
evaluations now classify the known witness and all 45 refinements, with exact
best-response absorption witnesses. A future randomized-disclosure study should
begin only after a separate ADR defines the experiment class, sender objective,
and solution object; it is not implied by the deterministic catalogue.

For DD-003, the registered accuracy perturbation is complete. The two-level base
and single three-color expansion establish exact full-pairwise counterexamples.
Any next step should pose a new bounded identification question---for example one
asymmetric prior or dependent-source law---and audit its state size before
expanding; no unbounded graph search follows automatically.

Longer-term work introduces feedback, overlapping coverage, mechanism design, and
empirical audits. Sequential search requires a stopping and information-update
model; greedy guarantees require submodularity or adaptive submodularity rather
than analogy \citep{NemhauserEtAl1978,GolovinKrause2011}. Mechanism design must
specify observability, budget balance, and credit. Empirical work must distinguish
descriptive concentration from an identified frontier or protocol-loss estimate.

Across these extensions, the evidence policy should remain constant: preregister
the feasible class and stopping rule, estimate the state space before computation,
preserve failed and null results, use immutable run identifiers, and promote
claims only after every proof, code, run, and test path has been audited.

\section{Conclusion}
% Claims: DD-C-0021, DD-C-0030, DD-C-0040, DD-C-0041, DD-C-0033, DD-C-0034, DD-C-0043, DD-C-0044, DD-C-0037, DD-C-0038
Three finite results expose three distinct ways a collective search can depart
from a symmetric direct protocol. Roles can reserve coverage without
communication; public disclosure can change a selected strategic outcome even as
the planner and pure equilibria improve, while alternative selection rules can
reject the same reversal; source networks can share complete first and pairwise
moments while producing different discovery once accuracy is represented as a
color.

The synthesis is deliberately qualified. The role counterexample is exact but
finite. The disclosure reversal is exact, selection-dependent, and not robust to
the other five audited evaluations. The homogeneous pairwise source result remains
a bounded null, while the heterogeneous colored class supplies an exact bounded
counterexample. The canonical private-team optimum is exact, but only for the
frozen zero-communication dimensions and symmetric signal law.

The shared lesson is architectural rather than universal: collective discovery
depends not only on what agents know, but on how roles are assigned, how strategic
outcomes are selected, and how source dependence is represented. Making those
margins explicit turns an appealing paradox into a sequence of falsifiable,
auditable research problems.

\bibliographystyle{plainnat}
{\raggedright\bibliography{generated/references}\par}
\end{document}
